### 2011-02-23 proposal/proposal.tex
initial import

\documentclass[a4paper]{article}
\usepackage{latexsym}
\usepackage[a4paper]{geometry}
\usepackage{color}
\usepackage{listings}
\usepackage[pdftex]{graphicx}
\usepackage{subfig}
\usepackage{amsmath}

%Boldface text for type writer font
\usepackage{bold-extra} %\DeclareFontShape{OT1}{cmtt}{bx}{n}{<5><6><7><8><9><10><10.95><12><14.4><17.28><20.74><24.88>cmttb10}{}

%Break words properly at the end of a line (which isn't sloppy...)
\sloppy

\title{\textsf{Context Inconsistency Management \\Using Partial Constraint Checking}}
\author{Samuel Esposito \and Alexander Jurjens}

\begin{document}
\maketitle

%% Abstract section.
\abstract{
Thanks to the pervasive computing paradigm more and more computer systems in utility buildings and industry are context-aware. They use a representation of the world they operate in to reduce the human-computer interaction necessary for this operation. Unfortunately reasoning based on contexts is not without flaws and context inconsistencies are the main reason for context-aware applications' incongruous behavior. Detecting context inconsistencies using traditional context modeling is very computer intensive, making timely conflict resolution unfeasible in most settings.\\
~\\
In this paper we present two complementary approaches for improving the mitigation of context inconsistencies. First we extend the traditional ontology based context modeling approach with context lifecycles to more accurately represent the world surrounding the application. Many of the conflicts in context reasoning can simply be resolved using information about the lifecycle state of a set of specific contexts. Secondly we propose partial constraint checking for more efficiently identifying and timely resolving context inconsistencies at runtime. By adding an extra constraint layer to the traditional ontology model, conflicts can be resolved by checking constraints or partial constraints only locally in the ontology. This dramatically improves performance compared to iterative evaluation of an entire ontology.\\
~\\
{\bf Keywords}: Pervasive Computing, Ontology Model, Context Lifecycle, Inconsistency Resolution\\
~\\
{\bf Field of Research}: Pervasive Computing
{\bf Topic}: Context Inconsistencies
{\bf Focus / Research Question}: Improving the detection and resolution of context inconsitencies
{\bf Expected Findings / Results}: The performance of conflict detection can dramatically be improved by partial constraint checking and the resolution of context conflicts is aided by adding lifecycle information to the ontology model.
} % end of abstract

\end{document}

### 2011-02-23 proposal/proposal.tex
add part about fuzzy owl to proposition

@@
 ~\\
+Apart from resolving conflicting contexts it is also possible to represent them into the ontology model.
+In our paper we explore the possibilities of incorporating inconsitencies into ontologies using fuzzy OWL and discuss the consequences of this approach on standard reasoning methods.\\
+~\\
 {\bf Keywords}: Pervasive Computing, Ontology Model, Context Lifecycle, Inconsistency Resolution\\

### 2011-02-28 proposal/proposal.tex
remove newline

@@
 By adding an extra constraint layer to the traditional ontology model, conflicts can be resolved by checking constraints or partial constraints only locally in the ontology.
-This dramatically improves performance compared to iterative evaluation of an entire ontology.\\
-~\\
+This dramatically improves performance compared to iterative evaluation of an entire ontology.
 Apart from resolving conflicting contexts it is also possible to represent them into the ontology model.

### 2011-02-28 paper/template.tex
initial import

\documentclass[journal]{vgtc}                % final (journal style)
%\documentclass[review,journal]{vgtc}         % review (journal style)
%\documentclass[widereview]{vgtc}             % wide-spaced review
%\documentclass[preprint,journal]{vgtc}       % preprint (journal style)
%\documentclass[electronic,journal]{vgtc}     % electronic version, journal

%% Uncomment one of the lines above depending on where your paper is
%% in the conference process. ``review'' and ``widereview'' are for review
%% submission, ``preprint'' is for pre-publication, and the final version
%% doesn't use a specific qualifier. Further, ``electronic'' includes
%% hyperreferences for more convenient online viewing.

%% Please use one of the ``review'' options in combination with the
%% assigned online id (see below) ONLY if your paper uses a double blind
%% review process. Some conferences, like IEEE Vis and InfoVis, have NOT
%% in the past.

%% Please note that the use of figures is not permitted on the first page
%% of the journal version.  Figures should begin on the second page and be
%% in CMYK or Grey scale format, otherwise, colour shifting may occur
%% during the printing process.  Papers submitted with figures on the
%% first page will be refused.

%% These three lines bring in essential packages: ``mathptmx'' for Type 1
%% typefaces, ``graphicx'' for inclusion of EPS figures. and ``times''
%% for proper handling of the times font family.

\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{times}

%% We encourage the use of mathptmx for consistent usage of times font
%% throughout the proceedings. However, if you encounter conflicts
%% with other math-related packages, you may want to disable it.

%% If you are submitting a paper to a conference for review with a double
%% blind reviewing process, please replace the value ``0'' below with your
%% OnlineID. Otherwise, you may safely leave it at ``0''.
\onlineid{0}

%% declare the category of your paper, only shown in review mode
\vgtccategory{Research}

%% allow for this line if you want the electronic option to work properly
\vgtcinsertpkg

%% In preprint mode you may define your own headline.
%\preprinttext{To appear in an IEEE VGTC sponsored conference.}

%% Paper title.

\title{Global Illumination for Fun and Profit}

%% This is how authors are specified in the journal style

%% indicate IEEE Member or Student Member in form indicated below
\author{Roy G. Biv, Ed Grimley, \textit{Member, IEEE}, and Martha Stewart}
\authorfooter{
%% insert punctuation at end of each item
\item
  Roy G. Biv is with Starbucks Research, E-mail: roy.g.biv@aol.com.
\item
  Ed Grimley is with Grimley Widgets, Inc., E-mail: ed.grimley@aol.com.
\item
  Martha Stewart is with Martha Stewart Enterprises at Microsoft
  Research, E-mail: martha.stewart@marthastewart.com.
}

%% A teaser figure is NOT to be included.

%other entries to be set up for journal
\shortauthortitle{Biv \MakeLowercase{\textit{et al.}}: Global Illumination for Fun and Profit}
%\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}

%% Abstract section.
\abstract{Duis autem vel eum iriure dolor in hendrerit in vulputate
velit esse molestie consequat, vel illum dolore eu feugiat nulla
facilisis at vero eros et accumsan et iusto odio dignissim qui blandit
praesent luptatum zzril delenit augue duis dolore te feugait nulla
facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit,
sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna
aliquam erat volutpat.

And this is what references look like~\cite{ware:2004:IVP}.

Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem
vel eum iriure dolor in hendrerit in vulputate velit esse molestie
consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et
accumsan et iusto odio dignissim qui blandit praesent luptatum zzril
delenit augue duis dolore te feugait nulla facilisi.
} % end of abstract

%% Keywords that describe your work. Will show as 'Index Terms' in journal
%% please capitalize first letter and insert punctuation after last keyword
\keywords{Radiosity, global illumination, constant time.}

%% ACM Computing Classification System (CCS). 
%% See <http://www.acm.org/class/1998/> for details.
%% The ``\CCScat'' command takes four arguments.

\CCScatlist{ % not used in journal version
  \CCScat{K.6.1}{Management of Computing and Information Systems}%
{Project and People Management}{Life Cycle};
  \CCScat{K.7.m}{The Computing Profession}{Miscellaneous}{Ethics}
}

%% Copyright space is enabled by default as required by guidelines.
%% It is disabled by the 'review' option or via the following command:
% \nocopyrightspace

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% START OF THE PAPER %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%% The ``\maketitle'' command must be the first command after the
%% ``\begin{document}'' command. It prepares and prints the title block.

%% the only exception to this rule is the \firstsection command
\firstsection{Introduction}

\maketitle

%% \section{Introduction} %for journal use above \firstsection{..} instead

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam
voluptua~\cite{kitware2003,Max:1995:OMF}. At vero eos et accusam et
justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
invidunt ut labore et dolore magna aliquyam erat, sed diam
voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet.

Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse
molestie consequat, vel illum dolore eu feugiat nulla facilisis at
vero eros et accumsan et iusto odio dignissim qui blandit praesent
luptatum zzril delenit augue duis dolore te feugait nulla
facilisi~\cite{notes2002}. Lorem ipsum dolor sit amet, consectetuer
adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet
dolore magna aliquam erat volutpat.

Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem
vel eum iriure dolor in hendrerit in vulputate velit esse molestie
consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et
accumsan et iusto odio dignissim qui blandit praesent luptatum zzril
delenit augue duis dolore te feugait nulla facilisi.

\section{Exposition}

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
invidunt ut labore et dolore magna aliquyam erat, sed diam
voluptua. At vero eos et accusam et justo duo dolores et ea
rebum~\cite{ware:2004:IVP}. Stet clita kasd gubergren, no sea takimata
sanctus est Lorem ipsum dolor sit amet.

Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse
molestie consequat, vel illum dolore eu feugiat nulla facilisis at
vero eros et accumsan et iusto odio dignissim qui blandit praesent
luptatum zzril delenit augue duis dolore te feugait nulla
facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit,
sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna
aliquam erat volutpat~\cite{kindlmann:1999:SAG}.

Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
suscipit lobortis nisl ut aliquip ex ea commodo
consequat~\cite{levoy:1989:DSV}. Duis autem vel eum iriure dolor in
hendrerit in vulputate velit esse molestie consequat, vel illum dolore
eu feugiat nulla facilisis at vero eros et accumsan et iusto odio
dignissim qui blandit praesent luptatum zzril delenit augue duis
dolore te feugait nulla facilisi.

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
invidunt ut labore et dolore magna aliquyam erat, sed diam
voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet.

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
invidunt ut labore et dolore magna aliquyam erat, sed diam
voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet.

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam voluptua.

\begin{equation}
 \sum_{j=1}^{z} j = \frac{z(z+1)}{2}
\end{equation}

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
invidunt ut labore et dolore magna aliquyam erat, sed diam
voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet.

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
invidunt ut labore et dolore magna aliquyam erat, sed diam
voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet.

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
takimata sanctus est Lorem ipsum dolor sit amet.

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
invidunt ut labore et dolore magna aliquyam erat, sed diam
voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet.

\begin{table}
%% Table captions on top in journal version
  \caption{Vis Paper Acceptance Rate}
  \label{vis_accept}
  \scriptsize
  \begin{center}
    \begin{tabular}{cccc}
      Year & Submitted & Accepted & Accepted (\%)\\
    \hline
      1994 &  91 & 41 & 45.1\\
      1995 & 102 & 41 & 40.2\\
      1996 & 101 & 43 & 42.6\\
      1997 & 117 & 44 & 37.6\\
      1998 & 118 & 50 & 42.4\\
      1999 & 129 & 47 & 36.4\\
      2000 & 151 & 52 & 34.4\\
      2001 & 152 & 51 & 33.6\\
      2002 & 172 & 58 & 33.7\\
      2003 & 192 & 63 & 32.8\\
      2004 & 167 & 46 & 27.6\\
      2005 & 268 & 88 & 32.8\\
      2006 & 228 & 63 & 27.6
    \end{tabular}
  \end{center}
\end{table}

\begin{figure}[htb]
  \centering
  \includegraphics[width=1.5in]{sample}
  \caption{Sample illustration.}
\end{figure}

\subsection{Mezcal Head}

Duis autem~\cite{Lorensen:1987:MCA} vel eum iriure dolor in hendrerit
in vulputate velit esse molestie consequat, vel illum dolore eu
feugiat nulla facilisis at vero eros et accumsan et iusto odio
dignissim qui blandit praesent luptatum zzril delenit augue duis
dolore te feugait nulla facilisi. Lorem ipsum dolor sit amet,
consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt
ut laoreet dolore magna aliquam erat volutpat%
\footnote{Footnotes appear at the bottom of the column}.

\subsubsection{Ejector Seat Reservation}

Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
suscipit lobortis nisl ut aliquip ex ea commodo
consequat~\cite{Nielson:1991:TAD}. Duis autem vel eum iriure dolor in
hendrerit in vulputate velit esse molestie consequat, vel illum dolore
eu feugiat nulla facilisis at vero eros et accumsan et iusto odio
dignissim qui blandit praesent luptatum zzril delenit augue duis
dolore te feugait nulla facilisi.

\paragraph{Rejected Ejector Seat Reservation}

Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem
vel eum iriure dolor in hendrerit in vulputate velit esse molestie

\section{Conclusion}

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
invidunt ut labore et dolore magna aliquyam erat, sed diam
voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet.

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
et justo duo dolores et ea rebum.

%% if specified like this the section will be ommitted in review mode
\acknowledgements{
The authors wish to thank A, B, C. This work was supported in part by
a grant from XYZ.}

\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{template}
\end{document}

### 2011-02-28 paper/paper.tex
add initial template

--- 2011-02-28 paper/template.tex
@@
 
-\title{Global Illumination for Fun and Profit}
+\title{Context Inconsistency Management \\Using Partial Constraint Checking}
 
@@
 %% indicate IEEE Member or Student Member in form indicated below
-\author{Roy G. Biv, Ed Grimley, \textit{Member, IEEE}, and Martha Stewart}
+\author{Samuel Esposito and Alexander Jurjens}
 \authorfooter{
@@
 %% Abstract section.
-\abstract{Duis autem vel eum iriure dolor in hendrerit in vulputate
-velit esse molestie consequat, vel illum dolore eu feugiat nulla
-facilisis at vero eros et accumsan et iusto odio dignissim qui blandit
-praesent luptatum zzril delenit augue duis dolore te feugait nulla
-facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit,
-sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna
-aliquam erat volutpat.
+\abstract{Thanks to the pervasive computing paradigm more and more computer systems in utility buildings and industry are context-aware.
+They use a representation of the world they operate in to reduce the human-computer interaction necessary for this operation.
+Unfortunately reasoning based on contexts is not without flaws and context inconsistencies are the main reason for context-aware applications' incongruous behavior.
+Detecting context inconsistencies using traditional context modeling is very computer intensive, making timely conflict resolution unfeasible in most settings.
 
-And this is what references look like~\cite{ware:2004:IVP}.
-
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
-suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem
-vel eum iriure dolor in hendrerit in vulputate velit esse molestie
-consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et
-accumsan et iusto odio dignissim qui blandit praesent luptatum zzril
-delenit augue duis dolore te feugait nulla facilisi.
+In this paper we present two complementary approaches for improving the mitigation of context inconsistencies.
+First we extend the traditional ontology based context modeling approach with context lifecycles to more accurately represent the world surrounding the application.
+Many of the conflicts in context reasoning can simply be resolved using information about the lifecycle state of a set of specific contexts.
+Secondly we propose partial constraint checking for more efficiently identifying and timely resolving context inconsistencies at runtime.
+By adding an extra constraint layer to the traditional ontology model, conflicts can be resolved by checking constraints or partial constraints only locally in the ontology.
+This dramatically improves performance compared to iterative evaluation of an entire ontology.
+Apart from resolving conflicting contexts it is also possible to represent them into the ontology model.
+In our paper we explore the possibilities of incorporating inconsitencies into ontologies using fuzzy OWL and discuss the consequences of this approach on standard reasoning methods.
 } % end of abstract
@@
 %% please capitalize first letter and insert punctuation after last keyword
-\keywords{Radiosity, global illumination, constant time.}
+\keywords{Pervasive Computing, Ontology Model, Context Lifecycle, Inconsistency Resolution.}
 

### 2011-03-03 paper/paper.tex
add initial references
cleanup template - add references

@@
 %% indicate IEEE Member or Student Member in form indicated below
-\author{Samuel Esposito and Alexander Jurjens}
-\authorfooter{
-%% insert punctuation at end of each item
-\item
-  Roy G. Biv is with Starbucks Research, E-mail: roy.g.biv@aol.com.
-\item
-  Ed Grimley is with Grimley Widgets, Inc., E-mail: ed.grimley@aol.com.
-\item
-  Martha Stewart is with Martha Stewart Enterprises at Microsoft
-  Research, E-mail: martha.stewart@marthastewart.com.
-}
-
-%% A teaser figure is NOT to be included.
-
-%other entries to be set up for journal
-\shortauthortitle{Biv \MakeLowercase{\textit{et al.}}: Global Illumination for Fun and Profit}
-%\shortauthortitle{Firstauthor \MakeLowercase{\textit{et al.}}: Paper Title}
+\author{Samuel Esposito ~~~~~~~~~~~~ Alexander Jurjens}
 
@@
 First we extend the traditional ontology based context modeling approach with context lifecycles to more accurately represent the world surrounding the application.
-Many of the conflicts in context reasoning can simply be resolved using information about the lifecycle state of a set of specific contexts.
+Many of the conflicts in context reasoning can simply be resolved using information about the lifecycle state of a set of specific contexts~\cite{bu:2006:CCM}.
 Secondly we propose partial constraint checking for more efficiently identifying and timely resolving context inconsistencies at runtime.
 By adding an extra constraint layer to the traditional ontology model, conflicts can be resolved by checking constraints or partial constraints only locally in the ontology.
-This dramatically improves performance compared to iterative evaluation of an entire ontology.
+This dramatically improves performance compared to iterative evaluation of an entire ontology~\cite{xu:2010:PCC}.
 Apart from resolving conflicting contexts it is also possible to represent them into the ontology model.
-In our paper we explore the possibilities of incorporating inconsitencies into ontologies using fuzzy OWL and discuss the consequences of this approach on standard reasoning methods.
+In our paper we explore the possibilities of incorporating inconsitencies into ontologies using fuzzy OWL and discuss the consequences of this approach on standard reasoning methods~\cite{ko:2009:IOFO}.
 } % end of abstract
@@
 \keywords{Pervasive Computing, Ontology Model, Context Lifecycle, Inconsistency Resolution.}
-
-%% ACM Computing Classification System (CCS). 
-%% See <http://www.acm.org/class/1998/> for details.
-%% The ``\CCScat'' command takes four arguments.
-
-\CCScatlist{ % not used in journal version
-  \CCScat{K.6.1}{Management of Computing and Information Systems}%
-{Project and People Management}{Life Cycle};
-  \CCScat{K.7.m}{The Computing Profession}{Miscellaneous}{Ethics}
-}
 
@@
 
-%% \section{Introduction} %for journal use above \firstsection{..} instead
+% WHAT
+Conflict detection\\
+Conflict resolution\\
+Inconsistent ontologies\\
+% WHY
+Performance\\
+Automate resolution\\
+Better model context\\
+% HOW
+PCC\\
+CIR\\
+HMM - Fuzzy set theory\\
 
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
-nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
-sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
-sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
-dolore magna aliquyam erat, sed diam
-voluptua~\cite{kitware2003,Max:1995:OMF}. At vero eos et accusam et
-justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
-takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
-amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
-invidunt ut labore et dolore magna aliquyam erat, sed diam
-voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet.
+\section{Related Work}
 
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse
-molestie consequat, vel illum dolore eu feugiat nulla facilisis at
-vero eros et accumsan et iusto odio dignissim qui blandit praesent
-luptatum zzril delenit augue duis dolore te feugait nulla
-facilisi~\cite{notes2002}. Lorem ipsum dolor sit amet, consectetuer
-adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet
-dolore magna aliquam erat volutpat.
+\section{Partial Constraint Checking}
 
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
-suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem
-vel eum iriure dolor in hendrerit in vulputate velit esse molestie
-consequat, vel illum dolore eu feugiat nulla facilisis at vero eros et
-accumsan et iusto odio dignissim qui blandit praesent luptatum zzril
-delenit augue duis dolore te feugait nulla facilisi.
+\section{Context Inconsistency Resolution}
 
-\section{Exposition}
+\section{Inconsistent Ontologies}
 
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
-nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
-sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
-sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
-dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
-et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
-takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
-amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
-invidunt ut labore et dolore magna aliquyam erat, sed diam
-voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum~\cite{ware:2004:IVP}. Stet clita kasd gubergren, no sea takimata
-sanctus est Lorem ipsum dolor sit amet.
-
-Duis autem vel eum iriure dolor in hendrerit in vulputate velit esse
-molestie consequat, vel illum dolore eu feugiat nulla facilisis at
-vero eros et accumsan et iusto odio dignissim qui blandit praesent
-luptatum zzril delenit augue duis dolore te feugait nulla
-facilisi. Lorem ipsum dolor sit amet, consectetuer adipiscing elit,
-sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna
-aliquam erat volutpat~\cite{kindlmann:1999:SAG}.
-
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
-suscipit lobortis nisl ut aliquip ex ea commodo
-consequat~\cite{levoy:1989:DSV}. Duis autem vel eum iriure dolor in
-hendrerit in vulputate velit esse molestie consequat, vel illum dolore
-eu feugiat nulla facilisis at vero eros et accumsan et iusto odio
-dignissim qui blandit praesent luptatum zzril delenit augue duis
-dolore te feugait nulla facilisi.
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
-nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
-sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
-sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
-dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
-et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
-takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
-amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
-invidunt ut labore et dolore magna aliquyam erat, sed diam
-voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet.
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
-nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
-sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
-sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
-dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
-et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
-takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
-amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
-invidunt ut labore et dolore magna aliquyam erat, sed diam
-voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet.
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
-nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
-sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
-sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
-dolore magna aliquyam erat, sed diam voluptua.
-
-\begin{equation}
- \sum_{j=1}^{z} j = \frac{z(z+1)}{2}
-\end{equation}
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
-nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
-sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
-sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
-dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
-et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
-takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
-amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
-invidunt ut labore et dolore magna aliquyam erat, sed diam
-voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet.
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
-nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
-sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
-sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
-dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
-et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
-takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
-amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
-invidunt ut labore et dolore magna aliquyam erat, sed diam
-voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet.
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
-nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
-sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
-sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
-dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
-et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
-takimata sanctus est Lorem ipsum dolor sit amet.
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
-nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
-sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
-sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
-dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
-et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
-takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
-amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
-invidunt ut labore et dolore magna aliquyam erat, sed diam
-voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet.
-
-\begin{table}
-%% Table captions on top in journal version
-  \caption{Vis Paper Acceptance Rate}
-  \label{vis_accept}
-  \scriptsize
-  \begin{center}
-    \begin{tabular}{cccc}
-      Year & Submitted & Accepted & Accepted (\%)\\
-    \hline
-      1994 &  91 & 41 & 45.1\\
-      1995 & 102 & 41 & 40.2\\
-      1996 & 101 & 43 & 42.6\\
-      1997 & 117 & 44 & 37.6\\
-      1998 & 118 & 50 & 42.4\\
-      1999 & 129 & 47 & 36.4\\
-      2000 & 151 & 52 & 34.4\\
-      2001 & 152 & 51 & 33.6\\
-      2002 & 172 & 58 & 33.7\\
-      2003 & 192 & 63 & 32.8\\
-      2004 & 167 & 46 & 27.6\\
-      2005 & 268 & 88 & 32.8\\
-      2006 & 228 & 63 & 27.6
-    \end{tabular}
-  \end{center}
-\end{table}
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=1.5in]{sample}
-  \caption{Sample illustration.}
-\end{figure}
-
-\subsection{Mezcal Head}
-
-Duis autem~\cite{Lorensen:1987:MCA} vel eum iriure dolor in hendrerit
-in vulputate velit esse molestie consequat, vel illum dolore eu
-feugiat nulla facilisis at vero eros et accumsan et iusto odio
-dignissim qui blandit praesent luptatum zzril delenit augue duis
-dolore te feugait nulla facilisi. Lorem ipsum dolor sit amet,
-consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt
-ut laoreet dolore magna aliquam erat volutpat%
-\footnote{Footnotes appear at the bottom of the column}.
-
-\subsubsection{Ejector Seat Reservation}
-
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
-suscipit lobortis nisl ut aliquip ex ea commodo
-consequat~\cite{Nielson:1991:TAD}. Duis autem vel eum iriure dolor in
-hendrerit in vulputate velit esse molestie consequat, vel illum dolore
-eu feugiat nulla facilisis at vero eros et accumsan et iusto odio
-dignissim qui blandit praesent luptatum zzril delenit augue duis
-dolore te feugait nulla facilisi.
-
-\paragraph{Rejected Ejector Seat Reservation}
-
-Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
-suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis autem
-vel eum iriure dolor in hendrerit in vulputate velit esse molestie
+\section{Discussion}
 
 \section{Conclusion}
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
-nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
-sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
-sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
-dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
-et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea
-takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit
-amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor
-invidunt ut labore et dolore magna aliquyam erat, sed diam
-voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet.
-
-Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam
-nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat,
-sed diam voluptua. At vero eos et accusam et justo duo dolores et ea
-rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem
-ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur
-sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et
-dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam
-et justo duo dolores et ea rebum.
-
-%% if specified like this the section will be ommitted in review mode
-\acknowledgements{
-The authors wish to thank A, B, C. This work was supported in part by
-a grant from XYZ.}
 
@@
 %\nocite{*}
-\bibliography{template}
+\bibliography{paper}
 \end{document}

### 2011-03-03 paper/paper.tex
add related work section

@@
 
-% WHAT
+- WHAT\\
 Conflict detection\\
@@
 Inconsistent ontologies\\
-% WHY
+~\\
+- WHY\\
 Performance\\
@@
 Better model context\\
-% HOW
+~\\
+- HOW\\
 PCC\\
@@
 \section{Related Work}
+Pervasive or ubiquitous computing is a fast-developing discipline that has been receiving increasing attention from both researchers and software developers~\cite{xu:2010:PCC}.
+In the past decade, many context-aware systems have been developed, ranging from smart room environments to warehouse and supply chain management systems.
+Lots of effort has been put into building middleware infrastructures that handle vast amounts of sensory data and extract the context information relevant for pervasive applications.
+Examples of such systems are CoBrA and CORTEX~\cite{bu:2006:CCM}.
+Various modeling approaches have been proposed for capturing context information, of which the ontology based context model appears to be most promising for most pervasive applications~\cite{bu:2006:CCM}.
+
+Context management for consistency however has not been adequately studied in the existing literature.
+None of the studies on context-awareness discusses a way for detecting context inconsistencies for reliable pervasive computing~\cite{xu:2010:PCC, bu:2006:CCM}.
+Even though there has been related research going on in other disciplines as artificial intelligence and software engineering, it doesn't provide adequate support for context inconsistency detection in ubuquitous computing.
+In addition the strategies proposed in literature for resolving context conflicts are not suited for pervasive computing.
+Some are based on assumptions that may not apply to general pervasive environments.
+Other require human participation for conflict resolution, which is usually expensive and slow for pervasive computing~\cite{xu:2010:PCC}.
+Finally no research has been done on the potential of fuzzy ontologies for representing context inconsistencies in the environment instead of trying to resolve them~\cite{ko:2009:IOFO}.
+
+In this article we aim at putting a milestone for context management by proposing an efficient inconsistency detection algorithm based on a constraint language extending the traditional ontology based context model.
+In addition we put forward a conflict resolution algorithm which is based on a context reliability heuristic.
+Finally the use of fuzzy ontologies representing context inconsistencies as a promising alternative to conflict resolution is explored.
 
@@
 
-\section{Inconsistent Ontologies}
+\section{Fuzzy Ontologies}
+
+better modeling
+training required
+maybe slower
+extensive research necessary
+
+HMM
+Forward-backward algorithm
 

### 2011-03-03 paper/paper.tex
tweak

@@
 
-In this article we aim at putting a milestone for context management by proposing an efficient inconsistency detection algorithm based on a constraint language extending the traditional ontology based context model.
-In addition we put forward a conflict resolution algorithm which is based on a context reliability heuristic.
+In this article we aim at putting a milestone for context management by presenting an efficient inconsistency detection algorithm based on a constraint language extending the traditional ontology based context model~\cite{xu:2010:PCC}.
+In addition we put forward a conflict resolution algorithm which is based on a context reliability heuristic~\cite{bu:2006:CCM}.
 Finally the use of fuzzy ontologies representing context inconsistencies as a promising alternative to conflict resolution is explored.

### 2011-03-03 paper/paper.tex
add pcc section

@@
 \section{Partial Constraint Checking}
+Constraint checking techniques have been extensively studied in software engineering.
+Existing constraint checking algorithms focus on checking software artifacts that do not change rapidly or frequently~\cite{xu:2010:PCC}.
+Context-aware applications require more efficient algorithms because they use a huge set of contexts wich can change very rapidly and frequently (in the range of miliseconds).
+An inefficient software solution for this does not only require massive computing power, but interestingly also induces a higher inconsistency detection miss rate: because of the computing delay conflicting contexts slip through the context buffer before they are detected by the software~\cite{xu:2010:PCC}.
+One example of an inefficient approach is nonincremental checking: whenever there is a change in the set of software artifacts these artifacts are each checked against the entire set of consistency constraints to find out all detectable inconsistencies.
+An improvement to this would be incremental checking: only a subset of all constraints are checked, namely those that are affected by the specific change in the artifact set.
+But the real merit of Xu and his colleagues was replacing the traditional entire constraint checking approach by partial contstraint checking based on a consistency computation tree~\cite{xu:2010:PCC}.
+Their idea is that constraints can be represented as trees with nodes for logical operations and leaves for specific properties of contexts or context sets.
+Whenever a context is added to or deleted from a context set in time, the branch corresponding to this context can respectively be added to or deleted from the tree.
+Because intermediate values are retained in the tree nodes after calculation they can be reused whenever the tree changes.
+More specifically, when a branch is added, only the values for the new branch itself and for the nodes from the branch top to the tree root need to be calculated.
+When a branch is deleted, only the values for the nodes from the branch top to the tree root have to be recalculated.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=3in]{cons_comp_tree}
+  \caption{Consistency Computation Tree: branches can be added or deleted to represent changes in a context set.}
+  \label{fig:cct}
+\end{figure}
 

### 2011-03-03 paper/paper.tex
finalize pcc section

@@
 An improvement to this would be incremental checking: only a subset of all constraints are checked, namely those that are affected by the specific change in the artifact set.
-But the real merit of Xu and his colleagues was replacing the traditional entire constraint checking approach by partial contstraint checking based on a consistency computation tree~\cite{xu:2010:PCC}.
+But the real merit of Xu et \textit{al.} was replacing the traditional entire constraint checking approach by partial contstraint checking based on a consistency computation tree.
 Their idea is that constraints can be represented as trees with nodes for logical operations and leaves for specific properties of contexts or context sets.
-Whenever a context is added to or deleted from a context set in time, the branch corresponding to this context can respectively be added to or deleted from the tree.
+Whenever a context is added to or deleted from a context set in time, the branch corresponding to this context can respectively be added to or deleted from the tree (see Fig.~\ref{fig:cct}).
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=3.5in]{cons_comp_tree}
+  \caption{Consistency Computation Tree: branches can be added or deleted to represent changes in a context set. Source:~\cite{xu:2010:PCC}}
+  \label{fig:cct}
+\end{figure}
 Because intermediate values are retained in the tree nodes after calculation they can be reused whenever the tree changes.
@@
 
+With their partial constraint checking algorithm Xu et \textit{al.} attained a time complexity between $O(n)$ for the worst case and $O(1)$ for the best case when a context was added to the set and $O(1)$ when a context was removed.
+Compared to traditional constraint checking with an overall complexity of $O(n)$, this is a dramatical improvement.
+In their experiments Xu et \textit{al.} showed that their performance is 15 times better than the traditional approach and in a case study the inconsistency miss rate dropped from $52.2\%$ in traditional checking to $0.1\%$ with partial checking~\cite{xu:2010:PCC}.
+
+\section{Context Inconsistency Resolution}
+
 \begin{figure}[htb]
   \centering
-  \includegraphics[width=3in]{cons_comp_tree}
-  \caption{Consistency Computation Tree: branches can be added or deleted to represent changes in a context set.}
-  \label{fig:cct}
+  \includegraphics[width=3.5in]{cir}
+  \caption{Context inconsistency resolution in action. Source:~\cite{bu:2006:CCM}}
+  \label{fig:cir}
 \end{figure}
-
-\section{Context Inconsistency Resolution}
 

### 2011-03-03 paper/paper.tex
add section about inconsistency resolution

@@
 Existing constraint checking algorithms focus on checking software artifacts that do not change rapidly or frequently~\cite{xu:2010:PCC}.
-Context-aware applications require more efficient algorithms because they use a huge set of contexts wich can change very rapidly and frequently (in the range of miliseconds).
+Context-aware applications require more efficient algorithms because they use a huge set of contexts, wich can change very rapidly and frequently (in the range of miliseconds).
 An inefficient software solution for this does not only require massive computing power, but interestingly also induces a higher inconsistency detection miss rate: because of the computing delay conflicting contexts slip through the context buffer before they are detected by the software~\cite{xu:2010:PCC}.
@@
 An improvement to this would be incremental checking: only a subset of all constraints are checked, namely those that are affected by the specific change in the artifact set.
-But the real merit of Xu et \textit{al.} was replacing the traditional entire constraint checking approach by partial contstraint checking based on a consistency computation tree.
+But the real merit of Xu et \textit{al.} was replacing the traditional entire constraint checking approach by partial contstraint checking based on a consistency computation tree~\cite{xu:2010:PCC}.
 Their idea is that constraints can be represented as trees with nodes for logical operations and leaves for specific properties of contexts or context sets.
@@
 \section{Context Inconsistency Resolution}
-
+Now that we have an efficient method for detecting inconsistencies the task of resolving the conflicts remains.
+As discussed above the strategies for conflict resolution in literature are not very suited for pervasive computing because their assumptions do not apply or they require human participation~\cite{xu:2010:PCC}.
+What really is needed is an algorithm that in the case of a conflict between two or more contexts decides which context has the highest reliability and retains that context.
+Bu et \textit{al.} show us that this is possible through extending the ontology based context model with additional information about the context's status and temporal properties~\cite{bu:2006:CCM}.
+More specifically they propose an algorithm that for every conflict set retains the context with the highest \textit{relative frequency}: frequency of context updates relative to update interval and context age (see Fig.~\ref{fig:cir}).
 \begin{figure}[htb]
@@
 \end{figure}
+This is based on the assumption that contexts that are most stably perceived by a system are most likely to be correct.
+This assumption is applicable to most of the environments in which pervasive systems run and is applied in many domains as a domain specific approach~\cite{xu:2010:PCC}.
 

### 2011-03-03 paper/paper.tex
rewrite abstract for consistency

@@
 \abstract{Thanks to the pervasive computing paradigm more and more computer systems in utility buildings and industry are context-aware.
-They use a representation of the world they operate in to reduce the human-computer interaction necessary for this operation.
+They use a representation of the world they operate in to reduce the human-computer interaction necessary for their operation.
 Unfortunately reasoning based on contexts is not without flaws and context inconsistencies are the main reason for context-aware applications' incongruous behavior.
-Detecting context inconsistencies using traditional context modeling is very computer intensive, making timely conflict resolution unfeasible in most settings.
+Context consistency management is not adequately studied in existing literature and approaches for detecting and resolving context conflicts are not suited for pervasive computing~\cite{xu:2010:PCC}.
 
 In this paper we present two complementary approaches for improving the mitigation of context inconsistencies. 
-First we extend the traditional ontology based context modeling approach with context lifecycles to more accurately represent the world surrounding the application.
-Many of the conflicts in context reasoning can simply be resolved using information about the lifecycle state of a set of specific contexts~\cite{bu:2006:CCM}.
-Secondly we propose partial constraint checking for more efficiently identifying and timely resolving context inconsistencies at runtime.
-By adding an extra constraint layer to the traditional ontology model, conflicts can be resolved by checking constraints or partial constraints only locally in the ontology.
+First we present partial constraint checking for timely identifying context inconsistencies at runtime.
+An extra constraint layer is added to the traditional ontology based context model and conflicts can be detected by locally checking partial constraints in the ontology.
 This dramatically improves performance compared to iterative evaluation of an entire ontology~\cite{xu:2010:PCC}.
-Apart from resolving conflicting contexts it is also possible to represent them into the ontology model.
-In our paper we explore the possibilities of incorporating inconsitencies into ontologies using fuzzy OWL and discuss the consequences of this approach on standard reasoning methods~\cite{ko:2009:IOFO}.
+Secondly we discuss the extention of the traditional ontology model with context lifecycles to more accurately represent the environment of context-aware applications.
+This information can then be used to estimate the relative reliability of contexts in a conflict set and discard the contexts with lowest reliabilty~\cite{bu:2006:CCM}.
+Apart from resolving context conflicts it is also possible to represent inconsistencies into the context model itself.
+In this paper we explore the possibilities of incorporating inconsitencies into ontologies using fuzzy OWL and discuss the consequences of this approach on standard reasoning methods~\cite{ko:2009:IOFO}.
 } % end of abstract

### 2011-03-03 paper/paper.tex
add introduction

@@
 
-- WHAT\\
-Conflict detection\\
-Conflict resolution\\
-Inconsistent ontologies\\
-~\\
-- WHY\\
-Performance\\
-Automate resolution\\
-Better model context\\
-~\\
-- HOW\\
-PCC\\
-CIR\\
-HMM - Fuzzy set theory\\
+In pervasive computing, contexts are used to make applications perform a certain action.
+Contexts can be seen as pieces of environmental information, which the applications depend on.
+Sometimes contexts are not consistent due to crossreads and misreads.
+The correctness of the contexts can be checked by evaluating the consistency constraints associated to them.
+There are multiple ways to check for consistency constraints.
+Constaint checking techniques are split up in two classes: Non-incremental checking and incremental checking.
+Incremental checking consists also of two classes: Entire Constraint Checking and Partial Constraint Checking.
+Once inconsistent contexts have been detected, an algorithm can be used to select the correct contexts.
+The algoritms use specific datastructures, like ontology models, in order to resolve the inconsistencies.
+However, certain conflict resolving algorithms are too slow for use in practice.
+This paper describes a way to use an ontology model in combination with the Partial Constraint Checking algorithm in order to detect context inconsistencies fast enough, such that it can be used in practice.
 

### 2011-03-03 paper/Introduction.tex
add introduction

--- 2011-03-03 paper/paper.tex
@@
-\documentclass[journal]{vgtc}                % final (journal style)
-%\documentclass[review,journal]{vgtc}         % review (journal style)
-%\documentclass[widereview]{vgtc}             % wide-spaced review
-%\documentclass[preprint,journal]{vgtc}       % preprint (journal style)
-%\documentclass[electronic,journal]{vgtc}     % electronic version, journal
+\documentclass[a4paper,10pt]{report}
+\usepackage[utf8x]{inputenc}
 
-%% Uncomment one of the lines above depending on where your paper is
-%% in the conference process. ``review'' and ``widereview'' are for review
-%% submission, ``preprint'' is for pre-publication, and the final version
-%% doesn't use a specific qualifier. Further, ``electronic'' includes
-%% hyperreferences for more convenient online viewing.
-
-%% Please use one of the ``review'' options in combination with the
-%% assigned online id (see below) ONLY if your paper uses a double blind
-%% review process. Some conferences, like IEEE Vis and InfoVis, have NOT
-%% in the past.
-
-%% Please note that the use of figures is not permitted on the first page
-%% of the journal version.  Figures should begin on the second page and be
-%% in CMYK or Grey scale format, otherwise, colour shifting may occur
-%% during the printing process.  Papers submitted with figures on the
-%% first page will be refused.
-
-%% These three lines bring in essential packages: ``mathptmx'' for Type 1
-%% typefaces, ``graphicx'' for inclusion of EPS figures. and ``times''
-%% for proper handling of the times font family.
-
-\usepackage{mathptmx}
-\usepackage{graphicx}
-\usepackage{times}
-
-%% We encourage the use of mathptmx for consistent usage of times font
-%% throughout the proceedings. However, if you encounter conflicts
-%% with other math-related packages, you may want to disable it.
-
-%% If you are submitting a paper to a conference for review with a double
-%% blind reviewing process, please replace the value ``0'' below with your
-%% OnlineID. Otherwise, you may safely leave it at ``0''.
-\onlineid{0}
-
-%% declare the category of your paper, only shown in review mode
-\vgtccategory{Research}
-
-%% allow for this line if you want the electronic option to work properly
-\vgtcinsertpkg
-
-%% In preprint mode you may define your own headline.
-%\preprinttext{To appear in an IEEE VGTC sponsored conference.}
-
-%% Paper title.
-
-\title{Context Inconsistency Management \\Using Partial Constraint Checking}
-
-%% This is how authors are specified in the journal style
-
-%% indicate IEEE Member or Student Member in form indicated below
-\author{Samuel Esposito ~~~~~~~~~~~~ Alexander Jurjens}
-
-%% Abstract section.
-\abstract{Thanks to the pervasive computing paradigm more and more computer systems in utility buildings and industry are context-aware.
-They use a representation of the world they operate in to reduce the human-computer interaction necessary for their operation.
-Unfortunately reasoning based on contexts is not without flaws and context inconsistencies are the main reason for context-aware applications' incongruous behavior.
-Context consistency management is not adequately studied in existing literature and approaches for detecting and resolving context conflicts are not suited for pervasive computing~\cite{xu:2010:PCC}.
-
-In this paper we present two complementary approaches for improving the mitigation of context inconsistencies. 
-First we present partial constraint checking for timely identifying context inconsistencies at runtime.
-An extra constraint layer is added to the traditional ontology based context model and conflicts can be detected by locally checking partial constraints in the ontology.
-This dramatically improves performance compared to iterative evaluation of an entire ontology~\cite{xu:2010:PCC}.
-Secondly we discuss the extention of the traditional ontology model with context lifecycles to more accurately represent the environment of context-aware applications.
-This information can then be used to estimate the relative reliability of contexts in a conflict set and discard the contexts with lowest reliabilty~\cite{bu:2006:CCM}.
-Apart from resolving context conflicts it is also possible to represent inconsistencies into the context model itself.
-In this paper we explore the possibilities of incorporating inconsitencies into ontologies using fuzzy OWL and discuss the consequences of this approach on standard reasoning methods~\cite{ko:2009:IOFO}.
-} % end of abstract
-
-%% Keywords that describe your work. Will show as 'Index Terms' in journal
-%% please capitalize first letter and insert punctuation after last keyword
-\keywords{Pervasive Computing, Ontology Model, Context Lifecycle, Inconsistency Resolution.}
-
-%% Copyright space is enabled by default as required by guidelines.
-%% It is disabled by the 'review' option or via the following command:
-% \nocopyrightspace
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%% START OF THE PAPER %%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Title Page
+\title{Introduction}
+\author{Alex en Sam}
 
 \begin{document}
+\maketitle
 
-%% The ``\maketitle'' command must be the first command after the
-%% ``\begin{document}'' command. It prepares and prints the title block.
+\begin{abstract}
+\end{abstract}
 
-%% the only exception to this rule is the \firstsection command
-\firstsection{Introduction}
-
-\maketitle
+\section{Introduction}
 
@@
 
-\section{Related Work}
-Pervasive or ubiquitous computing is a fast-developing discipline that has been receiving increasing attention from both researchers and software developers~\cite{xu:2010:PCC}.
-In the past decade, many context-aware systems have been developed, ranging from smart room environments to warehouse and supply chain management systems.
-Lots of effort has been put into building middleware infrastructures that handle vast amounts of sensory data and extract the context information relevant for pervasive applications.
-Examples of such systems are CoBrA and CORTEX~\cite{bu:2006:CCM}.
-Various modeling approaches have been proposed for capturing context information, of which the ontology based context model appears to be most promising for most pervasive applications~\cite{bu:2006:CCM}.
-
-Context management for consistency however has not been adequately studied in the existing literature.
-None of the studies on context-awareness discusses a way for detecting context inconsistencies for reliable pervasive computing~\cite{xu:2010:PCC, bu:2006:CCM}.
-Even though there has been related research going on in other disciplines as artificial intelligence and software engineering, it doesn't provide adequate support for context inconsistency detection in ubuquitous computing.
-In addition the strategies proposed in literature for resolving context conflicts are not suited for pervasive computing.
-Some are based on assumptions that may not apply to general pervasive environments.
-Other require human participation for conflict resolution, which is usually expensive and slow for pervasive computing~\cite{xu:2010:PCC}.
-Finally no research has been done on the potential of fuzzy ontologies for representing context inconsistencies in the environment instead of trying to resolve them~\cite{ko:2009:IOFO}.
-
-In this article we aim at putting a milestone for context management by presenting an efficient inconsistency detection algorithm based on a constraint language extending the traditional ontology based context model~\cite{xu:2010:PCC}.
-In addition we put forward a conflict resolution algorithm which is based on a context reliability heuristic~\cite{bu:2006:CCM}.
-Finally the use of fuzzy ontologies representing context inconsistencies as a promising alternative to conflict resolution is explored.
-
-\section{Partial Constraint Checking}
-Constraint checking techniques have been extensively studied in software engineering.
-Existing constraint checking algorithms focus on checking software artifacts that do not change rapidly or frequently~\cite{xu:2010:PCC}.
-Context-aware applications require more efficient algorithms because they use a huge set of contexts, wich can change very rapidly and frequently (in the range of miliseconds).
-An inefficient software solution for this does not only require massive computing power, but interestingly also induces a higher inconsistency detection miss rate: because of the computing delay conflicting contexts slip through the context buffer before they are detected by the software~\cite{xu:2010:PCC}.
-One example of an inefficient approach is nonincremental checking: whenever there is a change in the set of software artifacts these artifacts are each checked against the entire set of consistency constraints to find out all detectable inconsistencies.
-An improvement to this would be incremental checking: only a subset of all constraints are checked, namely those that are affected by the specific change in the artifact set.
-But the real merit of Xu et \textit{al.} was replacing the traditional entire constraint checking approach by partial contstraint checking based on a consistency computation tree~\cite{xu:2010:PCC}.
-Their idea is that constraints can be represented as trees with nodes for logical operations and leaves for specific properties of contexts or context sets.
-Whenever a context is added to or deleted from a context set in time, the branch corresponding to this context can respectively be added to or deleted from the tree (see Fig.~\ref{fig:cct}).
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=3.5in]{cons_comp_tree}
-  \caption{Consistency Computation Tree: branches can be added or deleted to represent changes in a context set. Source:~\cite{xu:2010:PCC}}
-  \label{fig:cct}
-\end{figure}
-Because intermediate values are retained in the tree nodes after calculation they can be reused whenever the tree changes.
-More specifically, when a branch is added, only the values for the new branch itself and for the nodes from the branch top to the tree root need to be calculated.
-When a branch is deleted, only the values for the nodes from the branch top to the tree root have to be recalculated.
-
-With their partial constraint checking algorithm Xu et \textit{al.} attained a time complexity between $O(n)$ for the worst case and $O(1)$ for the best case when a context was added to the set and $O(1)$ when a context was removed.
-Compared to traditional constraint checking with an overall complexity of $O(n)$, this is a dramatical improvement.
-In their experiments Xu et \textit{al.} showed that their performance is 15 times better than the traditional approach and in a case study the inconsistency miss rate dropped from $52.2\%$ in traditional checking to $0.1\%$ with partial checking~\cite{xu:2010:PCC}.
-
-\section{Context Inconsistency Resolution}
-Now that we have an efficient method for detecting inconsistencies the task of resolving the conflicts remains.
-As discussed above the strategies for conflict resolution in literature are not very suited for pervasive computing because their assumptions do not apply or they require human participation~\cite{xu:2010:PCC}.
-What really is needed is an algorithm that in the case of a conflict between two or more contexts decides which context has the highest reliability and retains that context.
-Bu et \textit{al.} show us that this is possible through extending the ontology based context model with additional information about the context's status and temporal properties~\cite{bu:2006:CCM}.
-More specifically they propose an algorithm that for every conflict set retains the context with the highest \textit{relative frequency}: frequency of context updates relative to update interval and context age (see Fig.~\ref{fig:cir}).
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=3.5in]{cir}
-  \caption{Context inconsistency resolution in action. Source:~\cite{bu:2006:CCM}}
-  \label{fig:cir}
-\end{figure}
-This is based on the assumption that contexts that are most stably perceived by a system are most likely to be correct.
-This assumption is applicable to most of the environments in which pervasive systems run and is applied in many domains as a domain specific approach~\cite{xu:2010:PCC}.
-
-\section{Fuzzy Ontologies}
-
-better modeling
-training required
-maybe slower
-extensive research necessary
-
-HMM
-Forward-backward algorithm
-
-\section{Discussion}
-
-\section{Conclusion}
-
-\bibliographystyle{abbrv}
-%%use following if all content of bibtex file should be shown
-%\nocite{*}
-\bibliography{paper}
 \end{document}

### 2011-03-03 paper/paper.tex
start of fuzzy ontology section

@@
 \section{Fuzzy Ontologies}
+In pervasive computing traditionally first order logic is used to model the environment of an application.
+This results in a so called ontology based context model and every observation that does not exactly fit in this model results into a conflict that leads to misadjusted behavior in applications unless they are timely detected and resolved~\cite{xu:2010:PCC}.
+Because it is impossible to perfectly model the unpredictive environment in which context-aware applications run, it would be nice if the context model was more resilient to unexpected observations.
+As we illustrate in the case study below, this can be obtained by using fuzzy ontologies.
+\subsection{Case Study}
+Suppose we want to build a context-aware application that has certain notion of teacher's activities to assist them in the best possible way (for instance automatically opening slides when a lecture starts).
+In the traditional approach we could build an ontology specifying where lectures take place that a lecture starts when the teacher stands at the lectern.
+If now an unpredicted observation is made (sensor cross read or teacher momentarily leaves the room), an inconsistency occurs that has to be resolved for the application to proceed normally.
+In the fuzzy ontology approach these unpredictive events can simply be modeled so that the ontology is more robust and always yields the most apt interpretation of the environment.
+A simplified example of such an ontology is depicted in Fig.~\ref{fig:fuzzy}.
 

### 2011-03-03 paper/paper.tex
add fuzzy ontology section

@@
 Suppose we want to build a context-aware application that has certain notion of teacher's activities to assist them in the best possible way (for instance automatically opening slides when a lecture starts).
-In the traditional approach we could build an ontology specifying where lectures take place that a lecture starts when the teacher stands at the lectern.
-If now an unpredicted observation is made (sensor cross read or teacher momentarily leaves the room), an inconsistency occurs that has to be resolved for the application to proceed normally.
-In the fuzzy ontology approach these unpredictive events can simply be modeled so that the ontology is more robust and always yields the most apt interpretation of the environment.
+In the traditional approach we could build an ontology specifying where lectures take place and that a lecture starts when the teacher appears at the lectern.
+If now an unpredicted observation is made (sensor cross read or teacher momentarily leaves the room), an inconsistency occurs that has to be resolved for the application to proceed with normal operation.
+In the fuzzy ontology approach these unpredictive events can simply be modeled so that the ontology is more robust and always yields the most apt interpretation of the environment without conflict resolution.
 A simplified example of such an ontology is depicted in Fig.~\ref{fig:fuzzy}.
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=3.5in]{fuzzy}
+  \caption{Fuzzy ontology specifying teachers activities and their most probable location.}
+  \label{fig:fuzzy}
+\end{figure}
+Using this fuzzy ontology the relative probability of each specified higher-level context can be calculated from the contexts in the observation window.
+For instance the observation sequence [$L_1$, $L_2$, $L_3$, $A_1$, $A_2$] gives a relative probability of 0.9998 for `Lecturing' and 0.0002 for `Working', event though the observations are clearly conflicting, since the teacher clearly cannot be at the lectern and in the aisle at the same time.
+The sequence of [$L_1$, $A_1$, $A_2$, $O_1$, $O_2$] gives a 0.941 probability for `Working' and 0.059 for `Lecturing', even though the teacher stricly spoken cannot be at the lectern and in the office at the same time (see appendix for exact calculations).
+Regardless to the inconsistencies in the observed contexts the fuzzy ontology always yields the most probable higher-level context without the need for conflict detection and resolution.
+
+Interestingly the fuzzy ontology has some tree-like structure that allows for very efficient incremental partial probability calculation.
+The probability of a higher-level context is calculated by simply multiplying the probabilities of the observed contexts.
+When a new context is added to the observation window, the intermediate calculation result stored at a node (the root in Fig.~\ref{fig:fuzzy}) can simply be multiplied by de probability of the new observation in order to obtain the updated probability for a higher-level context.
+When a context dissapears from the observation window, the intermediate result can simply be divided by the context's probability to obtain an updated probability for a higher-leve context.
+
+Note that it is possible to extend this simple fuzzy ontology with start and transition probabilities for the higher-level contexts as in hidden markov models\footnote{http://en.wikipedia.org/wikiHidden\_Markov\_model} and other information such as the expected lecture time window (also fuzzy of course).
 
@@
 
+\section{provisory appendix}
+
+[$L_1$, $L_2$, $L_3$, $A_1$, $A_2$] 
+Lecturing
+= .8 * .8 * .8 * .15 * .15 * c1
+= .01152 * c1
+= 0.9998
+Working
+= .05 * .05 * .05 * .15 * .15 * c1
+= 0.000002813 * c1
+= 0.0002
+
+[$L_1$, $A_1$, $A_2$, $O_1$, $O_2$]
+Lecturing
+= .8 * .15 * .15 * .05 * .05 * c
+= 0.000045 * c
+= 0.059
+Working
+= .05 * .15 * .15 * .8 * .8 * c
+= 0.00072 * c
+= 0.941
+
 \bibliographystyle{abbrv}

### 2011-03-03 paper/paper.tex
add discussion and conclusion

@@
 The sequence of [$L_1$, $A_1$, $A_2$, $O_1$, $O_2$] gives a 0.941 probability for `Working' and 0.059 for `Lecturing', even though the teacher stricly spoken cannot be at the lectern and in the office at the same time (see appendix for exact calculations).
-Regardless to the inconsistencies in the observed contexts the fuzzy ontology always yields the most probable higher-level context without the need for conflict detection and resolution.
 
-Interestingly the fuzzy ontology has some tree-like structure that allows for very efficient incremental partial probability calculation.
+\subsection{Results}
+Regardless of any inconsistencies in the observed contexts a fuzzy ontology always yields the most probable higher-level context without the need for conflict detection and resolution.
+
+Interestingly a fuzzy ontology has some tree-like structure that allows for very efficient incremental partial probability calculation (PPC).
 The probability of a higher-level context is calculated by simply multiplying the probabilities of the observed contexts.
-When a new context is added to the observation window, the intermediate calculation result stored at a node (the root in Fig.~\ref{fig:fuzzy}) can simply be multiplied by de probability of the new observation in order to obtain the updated probability for a higher-level context.
-When a context dissapears from the observation window, the intermediate result can simply be divided by the context's probability to obtain an updated probability for a higher-leve context.
+When a new context is added to the observation window, the intermediate calculation result stored at a node (the root in our case study) can simply be multiplied by de probability of the new observation in order to obtain the updated probability for a higher-level context.
+When a context dissapears from the observation window, the intermediate result can simply be divided by the context's probability to obtain an updated probability for a higher-level context.
 
-Note that it is possible to extend this simple fuzzy ontology with start and transition probabilities for the higher-level contexts as in hidden markov models\footnote{http://en.wikipedia.org/wikiHidden\_Markov\_model} and other information such as the expected lecture time window (also fuzzy of course).
+Note that it is possible to extend the simple fuzzy ontology from the use case by specifying start and transition probabilities for the higher-level contexts, just as hidden markov models\footnote{http://en.wikipedia.org/wikiHidden\_Markov\_model} do, and other information such as the expected lecture time window (fuzzified of course~\cite{Buckley1995245}).
 
@@
 \section{Discussion}
+In this article we started with presenting partial constraint checking: an efficient algorithm for timely detecting inconsistencies in huge sets of contexts which change very frequently.
+Partial constraint checking was 15 times as efficient as the traditional gready approach and reduced the conflict detection miss rate from 52.2\% to 0.1\%.
+This algorithm is clearly a dramatic improvement of the traditional approach and vital to any context aware application that has to handle high-frequently generated contexts.
+
+After that we shed light on ways to resolve the detected conflicts and discussed a context inconsistency resolution algorithm that estimates the reliability of conflicting contexts and only retains the most reliable context from every conflict set.
+Using this algorithm allows for timely conflict resolution at runtime without the need for human participation.
+The algorithm is a valuable addition to the research on conflict resolution in pervasive computing, but when applying it one has to verify the aptness of the heuristic used for context reliability estimations in the domain at hand.
+In particular the assumption that contexts with the highest relative frequency are most reliable has to apply in the domain.
+
+Finally the use of fuzzy ontologies for modeling the environment of context-aware applications seems promising.
+By incorporating possible inconsistencies in the model the need for context inconsistency management vanishes, vastly reducing the complexity of the used middleware.
+Fuzzy ontologies always yield the most probable higher-level contexts, regardless of the inconsistencies in the observed context set.
+In addition the calculation of the probabilities in a fuzzy ontology has great potential for optimization by using incremental partial probability calculation.
+When using fuzzy ontologies one however has to take into account the required training of the system for obtaining well defined probabilities in the context model.
 
 \section{Conclusion}
+In conclusion we can say that the partial constraint checking algorithm can dramatically improve the performance of context-aware applications where context consistency management is needed.
+With this performance improvement we get an impressive reduction of missed context inconsistencies for free.
+The context inconsistency resolution algorithm is a good solution in most domains for timely resolving context conflicts without human intervention.
+The fuzzy ontology approach seems a promising alternative to traditional context modeling but needs extensive further research in order to determine its real value in context-aware applications.
 

### 2011-03-14 paper/paper.tex
add appendix
change title
update abstract and proposal

@@
 \usepackage{times}
+\usepackage{amsmath}
 
@@
 
-\title{Context Inconsistency Management \\Using Partial Constraint Checking}
+\title{Context Inconsistency Management \\in Pervasive Systems}
 
@@
 This information can then be used to estimate the relative reliability of contexts in a conflict set and discard the contexts with lowest reliabilty~\cite{bu:2006:CCM}.
-Apart from resolving context conflicts it is also possible to represent inconsistencies into the context model itself.
-In this paper we explore the possibilities of incorporating inconsitencies into ontologies using fuzzy OWL and discuss the consequences of this approach on standard reasoning methods~\cite{ko:2009:IOFO}.
+Apart from resolving context conflicts it is also possible to represent inconsistencies into the context model itself~\cite{ko:2009:IOFO}.
+In this paper we present a use case in which we explore the possibilities of incorporating inconsitencies into context models using fuzzy ontologies.
 } % end of abstract
@@
 
-better modeling
-training required
-maybe slower
-extensive research necessary
-
-HMM
-Forward-backward algorithm
-
 \section{Discussion}
@@
 
-\section{provisory appendix}
-
-[$L_1$, $L_2$, $L_3$, $A_1$, $A_2$] 
-Lecturing
-= .8 * .8 * .8 * .15 * .15 * c1
-= .01152 * c1
-= 0.9998
-Working
-= .05 * .05 * .05 * .15 * .15 * c1
-= 0.000002813 * c1
-= 0.0002
-
-[$L_1$, $A_1$, $A_2$, $O_1$, $O_2$]
-Lecturing
-= .8 * .15 * .15 * .05 * .05 * c
-= 0.000045 * c
-= 0.059
-Working
-= .05 * .15 * .15 * .8 * .8 * c
-= 0.00072 * c
-= 0.941
-
 \bibliographystyle{abbrv}
@@
 \bibliography{paper}
+
+\appendix
+\section{Fuzzy Ontology Calculations}
+Observed Context Set 1: $[L_1, L_2, L_3, A_1, A_2]$
+\begin{align}
+                          Lecturing &= .8 * .8 * .8 * .15 * .15 * c_1\\
+                                    &= .01152 * c_1\\
+                                    &= 0.9998\\
+                            Working &= .05 * .05 * .05 * .15 * .15 * c_1\\
+                                    &= 0.000002813 * c_1\\
+                                    &= 0.0002\\
+\end{align}
+Observed Context Set 2: $[L_1, A_1, A_2, O_1, O_2]$
+\begin{align}
+                          Lecturing &= .8 * .15 * .15 * .05 * .05 * c_2\\
+                                    &= 0.000045 * c_2\\
+                                    &= 0.059\\
+                            Working &= .05 * .15 * .15 * .8 * .8 * c_2\\
+                                    &= 0.00072 * c_2\\
+                                    &= 0.941\\
+\end{align}
 \end{document}

### 2011-03-14 proposal/proposal.tex
update abstract and proposal

--- 2011-02-23 proposal/proposal.tex
@@
 Thanks to the pervasive computing paradigm more and more computer systems in utility buildings and industry are context-aware.
-They use a representation of the world they operate in to reduce the human-computer interaction necessary for this operation.
+They use a representation of the world they operate in to reduce the human-computer interaction necessary for their operation.
 Unfortunately reasoning based on contexts is not without flaws and context inconsistencies are the main reason for context-aware applications' incongruous behavior.
-Detecting context inconsistencies using traditional context modeling is very computer intensive, making timely conflict resolution unfeasible in most settings.\\
-~\\
-In this paper we present two complementary approaches for improving the mitigation of context inconsistencies.
-First we extend the traditional ontology based context modeling approach with context lifecycles to more accurately represent the world surrounding the application.
-Many of the conflicts in context reasoning can simply be resolved using information about the lifecycle state of a set of specific contexts.
-Secondly we propose partial constraint checking for more efficiently identifying and timely resolving context inconsistencies at runtime.
-By adding an extra constraint layer to the traditional ontology model, conflicts can be resolved by checking constraints or partial constraints only locally in the ontology.
-This dramatically improves performance compared to iterative evaluation of an entire ontology.\\
+Context consistency management is not adequately studied in existing literature and approaches for detecting and resolving context conflicts are not suited for pervasive computing.
+
+In our paper we present two complementary approaches for improving the mitigation of context inconsistencies. 
+First we present partial constraint checking for timely identifying context inconsistencies at runtime.
+An extra constraint layer is added to the traditional ontology based context model and conflicts can be detected by locally checking partial constraints in the ontology.
+This dramatically improves performance compared to iterative evaluation of an entire ontology.
+Secondly we discuss the extention of the traditional ontology model with context lifecycles to more accurately represent the environment of context-aware applications.
+This information can then be used to estimate the relative reliability of contexts in a conflict set and discard the contexts with lowest reliabilty.
+Apart from resolving context conflicts it is also possible to represent inconsistencies into the context model itself.
+In our paper we present a use case in which we explore the possibilities of incorporating inconsitencies into context models using fuzzy ontologies.\\
 ~\\

### 2011-03-20 proposal/proposal.tex
rework proposal wrt feedback

@@
 ~\\
-{\bf Field of Research}: Pervasive Computing
-{\bf Topic}: Context Inconsistencies
-{\bf Focus / Research Question}: Improving the detection and resolution of context inconsitencies
-{\bf Expected Findings / Results}: The performance of conflict detection can dramatically be improved by partial constraint checking and the resolution of context conflicts is aided by adding lifecycle information to the ontology model.
+{\bf Field of Research}: Pervasive Computing\\
+{\bf Topic}: Context Inconsistencies\\
+{\bf Focus / Research Question}: Improving the detection and resolution of context inconsitencies. Exploring the use of fuzzy ontologies for modeling contexts.\\
+{\bf Expected Findings / Results}: The performance of conflict detection can dramatically be improved by using partial constraint checking.
+The resolution of context conflicts is aided by adding lifecycle information to the ontology model.
+Fuzzy ontology modeling is a promising alternative to the traditional approach of context inconsistency mitigation.
 } % end of abstract

### 2011-03-21 paper/paper.tex
extend introduction
some tweaks - pdfify
add section

@@
 This paper describes a way to use an ontology model in combination with the Partial Constraint Checking algorithm in order to detect context inconsistencies fast enough, such that it can be used in practice.
+Another approach to handling context inconsistencies is representing them into the context model, as opposed to resolving them.
+This can be done efficiently by using fuzzy ontologies in a tree like structure, as we show in a use case.
 
@@
 In their experiments Xu et \textit{al.} showed that their performance is 15 times better than the traditional approach and in a case study the inconsistency miss rate dropped from $52.2\%$ in traditional checking to $0.1\%$ with partial checking~\cite{xu:2010:PCC}.
+
+\section{From Ontology to CCT}
+As stated above the Partial Constraint Checking (PCC) algorithm is much faster than Entire Constraint Checking due to the fact that a Consistency Computation Tree (CCT) is used to store the constraints belonging to a (set of) context(s).
+We also stated that the ontology based context model is the most promising type of model to capture context information.
+Although the context model appears as a tree (see Fig.
+\ref{fig:ont}), the PCC algorithm cannot be directly applied to it.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=3.5in]{Ontology.eps}
+  \caption{An example of an ontology based context model Source:~\cite{bu:2006:CCM}}
+  \label{fig:ont}
+\end{figure}
+
+The model is actually a part of a larger ontology, but it is sufficient for this section.
+Now it needs to be transformed into a CCT for PCC.
+With a CCT the main focus should be on the context set of a single entity in the model.
+The transformation itself can be done automatically with a depth-first search algorithm, but there is no such algorithm available at this time.
+However, we can give a few examples of the CCT based on this ontology model.
+The context set of the entity \textit{Student} will be focused on.
+Lets say that the entity \textit{Student} is located in the \textit{Place} entity \textit{Road}, then the CCT will look as the upper tree in Fig.
+\ref{fig:cct1}.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=3.5in]{smallCCT1.eps}
+  \caption{The CCTs of \textit{Student}}
+  \label{fig:cct1}
+\end{figure}
+
+If the system suddenly decides that \textit{Student} is located in a \textit{Lab}, then the tree will be updated to the lower tree.
+Note that the system can decide in a multitude of ways that \textit{Student} is located in the \textit{Lab} by for example invalidating the earlier constraint branch after a certain amount of time or by for example basing the new \textit{Place} on the information in a new context set.
+Also note that the leaf of a branch cannot contain an entity that is not available in the context model.
+So \textit{Student} cannot be located in, for example, \textit{Car}, because it is not part of the model.
+Even if the location in a context would be \textit{Car}, then the system would consider the location as an inconsistency in the context and detect it very quickly with PCC.
 
@@
 
+Then we have shown examples of CCTs of entitities in an ontology based context model.
+We have not shown an algorithm on how to do this efficiently as we don't know the formal definition of OWL at this point in time.
+However, with the definitions of OWL one can create a depth-first search algorithm that transforms an ontology in multiple CCTs (one for each leaf entity in the model).
+
 After that we shed light on ways to resolve the detected conflicts and discussed a context inconsistency resolution algorithm that estimates the reliability of conflicting contexts and only retains the most reliable context from every conflict set.
@@
 \bibliography{paper}
-
+\newpage
 \appendix
@@
                                     &= 0.000002813 * c_1\\
-                                    &= 0.0002\\
+                                    &= 0.0002
 \end{align}
@@
                                     &= 0.00072 * c_2\\
-                                    &= 0.941\\
+                                    &= 0.941
 \end{align}

### 2011-04-07 paper/paper.tex
add review docs - review for spelling and fix references

@@
 Contexts can be seen as pieces of environmental information, which the applications depend on.
-Sometimes contexts are not consistent due to crossreads and misreads.
+Sometimes contexts are not consistent due to cross reads and misreads.
 The correctness of the contexts can be checked by evaluating the consistency constraints associated to them.
 There are multiple ways to check for consistency constraints.
-Constaint checking techniques are split up in two classes: Non-incremental checking and incremental checking.
+Constraint checking techniques are split up in two classes: Non-incremental checking and incremental checking.
 Incremental checking consists also of two classes: Entire Constraint Checking and Partial Constraint Checking.
 Once inconsistent contexts have been detected, an algorithm can be used to select the correct contexts.
-The algoritms use specific datastructures, like ontology models, in order to resolve the inconsistencies.
+The algorithms use specific data structures, like ontology models, in order to resolve the inconsistencies.
 However, certain conflict resolving algorithms are too slow for use in practice.
@@
 Lots of effort has been put into building middleware infrastructures that handle vast amounts of sensory data and extract the context information relevant for pervasive applications.
-Examples of such systems are CoBrA and CORTEX~\cite{bu:2006:CCM}.
+Examples of such systems are CoBrA~\cite{1276865} and CORTEX~\cite{1276875}.
 Various modeling approaches have been proposed for capturing context information, of which the ontology based context model appears to be most promising for most pervasive applications~\cite{bu:2006:CCM}.
@@
 None of the studies on context-awareness discusses a way for detecting context inconsistencies for reliable pervasive computing~\cite{xu:2010:PCC, bu:2006:CCM}.
-Even though there has been related research going on in other disciplines as artificial intelligence and software engineering, it doesn't provide adequate support for context inconsistency detection in ubuquitous computing.
+Even though there has been related research going on in other disciplines as artificial intelligence and software engineering, it doesn't provide adequate support for context inconsistency detection in ubiquitous computing.
 In addition the strategies proposed in literature for resolving context conflicts are not suited for pervasive computing.
@@
 Existing constraint checking algorithms focus on checking software artifacts that do not change rapidly or frequently~\cite{xu:2010:PCC}.
-Context-aware applications require more efficient algorithms because they use a huge set of contexts, wich can change very rapidly and frequently (in the range of miliseconds).
+Context-aware applications require more efficient algorithms because they use a huge set of contexts, which can change very rapidly and frequently (in the range of milliseconds).
 An inefficient software solution for this does not only require massive computing power, but interestingly also induces a higher inconsistency detection miss rate: because of the computing delay conflicting contexts slip through the context buffer before they are detected by the software~\cite{xu:2010:PCC}.
-One example of an inefficient approach is nonincremental checking: whenever there is a change in the set of software artifacts these artifacts are each checked against the entire set of consistency constraints to find out all detectable inconsistencies.
+One example of an inefficient approach is non-incremental checking: whenever there is a change in the set of software artifacts these artifacts are each checked against the entire set of consistency constraints to find out all detectable inconsistencies.
 An improvement to this would be incremental checking: only a subset of all constraints are checked, namely those that are affected by the specific change in the artifact set.
-But the real merit of Xu et \textit{al.} was replacing the traditional entire constraint checking approach by partial contstraint checking based on a consistency computation tree~\cite{xu:2010:PCC}.
+But the real merit of Xu et \textit{al.} was replacing the traditional entire constraint checking approach by partial constraint checking based on a consistency computation tree~\cite{xu:2010:PCC}.
 Their idea is that constraints can be represented as trees with nodes for logical operations and leaves for specific properties of contexts or context sets.
@@
 This results in a so called ontology based context model and every observation that does not exactly fit in this model results into a conflict that leads to misadjusted behavior in applications unless they are timely detected and resolved~\cite{xu:2010:PCC}.
-Because it is impossible to perfectly model the unpredictive environment in which context-aware applications run, it would be nice if the context model was more resilient to unexpected observations.
+Because it is impossible to perfectly model the un-predictive environment in which context-aware applications run, it would be nice if the context model was more resilient to unexpected observations.
 As we illustrate in the case study below, this can be obtained by using fuzzy ontologies.
@@
 If now an unpredicted observation is made (sensor cross read or teacher momentarily leaves the room), an inconsistency occurs that has to be resolved for the application to proceed with normal operation.
-In the fuzzy ontology approach these unpredictive events can simply be modeled so that the ontology is more robust and always yields the most apt interpretation of the environment without conflict resolution.
+In the fuzzy ontology approach these unpredictable events can simply be modeled so that the ontology is more robust and always yields the most apt interpretation of the environment without conflict resolution.
 A simplified example of such an ontology is depicted in Fig.~\ref{fig:fuzzy}.
@@
 For instance the observation sequence [$L_1$, $L_2$, $L_3$, $A_1$, $A_2$] gives a relative probability of 0.9998 for `Lecturing' and 0.0002 for `Working', event though the observations are clearly conflicting, since the teacher clearly cannot be at the lectern and in the aisle at the same time.
-The sequence of [$L_1$, $A_1$, $A_2$, $O_1$, $O_2$] gives a 0.941 probability for `Working' and 0.059 for `Lecturing', even though the teacher stricly spoken cannot be at the lectern and in the office at the same time (see appendix for exact calculations).
+The sequence of [$L_1$, $A_1$, $A_2$, $O_1$, $O_2$] gives a 0.941 probability for `Working' and 0.059 for `Lecturing', even though the teacher strictly spoken cannot be at the lectern and in the office at the same time (see appendix for exact calculations).
 
@@
 When a new context is added to the observation window, the intermediate calculation result stored at a node (the root in our case study) can simply be multiplied by de probability of the new observation in order to obtain the updated probability for a higher-level context.
-When a context dissapears from the observation window, the intermediate result can simply be divided by the context's probability to obtain an updated probability for a higher-level context.
+When a context disappears from the observation window, the intermediate result can simply be divided by the context's probability to obtain an updated probability for a higher-level context.
 
-Note that it is possible to extend the simple fuzzy ontology from the use case by specifying start and transition probabilities for the higher-level contexts, just as hidden markov models\footnote{http://en.wikipedia.org/wikiHidden\_Markov\_model} do, and other information such as the expected lecture time window (fuzzified of course~\cite{Buckley1995245}).
+Note that it is possible to extend the simple fuzzy ontology from the use case by specifying start and transition probabilities for the higher-level contexts, just as hidden Markov models\footnote{http://en.wikipedia.org/wikiHidden\_Markov\_model} do, and other information such as the expected lecture time window (fuzzified of course~\cite{Buckley1995245}).
 
@@
 In this article we started with presenting partial constraint checking: an efficient algorithm for timely detecting inconsistencies in huge sets of contexts which change very frequently.
-Partial constraint checking was 15 times as efficient as the traditional gready approach and reduced the conflict detection miss rate from 52.2\% to 0.1\%.
+Partial constraint checking was 15 times as efficient as the traditional greedy approach and reduced the conflict detection miss rate from 52.2\% to 0.1\%.
 This algorithm is clearly a dramatic improvement of the traditional approach and vital to any context aware application that has to handle high-frequently generated contexts.
 
-Then we have shown examples of CCTs of entitities in an ontology based context model.
+Then we have shown examples of CCTs of entities in an ontology based context model.
 We have not shown an algorithm on how to do this efficiently as we don't know the formal definition of OWL at this point in time.

### 2011-04-07 paper/paper.tex
review for language

@@
 This dramatically improves performance compared to iterative evaluation of an entire ontology~\cite{xu:2010:PCC}.
-Secondly we discuss the extention of the traditional ontology model with context lifecycles to more accurately represent the environment of context-aware applications.
-This information can then be used to estimate the relative reliability of contexts in a conflict set and discard the contexts with lowest reliabilty~\cite{bu:2006:CCM}.
+Secondly we discuss the extension of the traditional ontology model with context life cycles to more accurately represent the environment of context-aware applications.
+This information can then be used to estimate the relative reliability of contexts in a conflict set and discard the contexts with lowest reliability~\cite{bu:2006:CCM}.
 Apart from resolving context conflicts it is also possible to represent inconsistencies into the context model itself~\cite{ko:2009:IOFO}.
-In this paper we present a use case in which we explore the possibilities of incorporating inconsitencies into context models using fuzzy ontologies.
+In this paper we present a use case in which we explore the possibilities of incorporating inconsistencies into context models using fuzzy ontologies.
 } % end of abstract
@@
 Constraint checking techniques are split up in two classes: Non-incremental checking and incremental checking.
-Incremental checking consists also of two classes: Entire Constraint Checking and Partial Constraint Checking.
+Incremental checking also consists of two classes: Entire Constraint Checking and Partial Constraint Checking.
 Once inconsistent contexts have been detected, an algorithm can be used to select the correct contexts.
@@
 In the past decade, many context-aware systems have been developed, ranging from smart room environments to warehouse and supply chain management systems.
-Lots of effort has been put into building middleware infrastructures that handle vast amounts of sensory data and extract the context information relevant for pervasive applications.
+A lot of effort has been put into building middleware infrastructures that handle vast amounts of sensory data and extract the context information relevant for pervasive applications.
 Examples of such systems are CoBrA~\cite{1276865} and CORTEX~\cite{1276875}.
@@
 None of the studies on context-awareness discusses a way for detecting context inconsistencies for reliable pervasive computing~\cite{xu:2010:PCC, bu:2006:CCM}.
-Even though there has been related research going on in other disciplines as artificial intelligence and software engineering, it doesn't provide adequate support for context inconsistency detection in ubiquitous computing.
+Even though other disciplines as artificial intelligence and software engineering conducted relate research, it does not provide adequate support for context inconsistency detection in ubiquitous computing.
 In addition the strategies proposed in literature for resolving context conflicts are not suited for pervasive computing.
@@
 Other require human participation for conflict resolution, which is usually expensive and slow for pervasive computing~\cite{xu:2010:PCC}.
-Finally no research has been done on the potential of fuzzy ontologies for representing context inconsistencies in the environment instead of trying to resolve them~\cite{ko:2009:IOFO}.
+Finally no research has been done on the potential of fuzzy ontologies to represent context inconsistencies in the environment instead of trying to resolve them~\cite{ko:2009:IOFO}.
 
@@
 Context-aware applications require more efficient algorithms because they use a huge set of contexts, which can change very rapidly and frequently (in the range of milliseconds).
-An inefficient software solution for this does not only require massive computing power, but interestingly also induces a higher inconsistency detection miss rate: because of the computing delay conflicting contexts slip through the context buffer before they are detected by the software~\cite{xu:2010:PCC}.
+An inefficient software solution for this does not only require massive computing power, but interestingly also induces a higher inconsistency detection miss rate.
+Because of the computing delay conflicting contexts slip through the context buffer before they are detected by the software~\cite{xu:2010:PCC}.
 One example of an inefficient approach is non-incremental checking: whenever there is a change in the set of software artifacts these artifacts are each checked against the entire set of consistency constraints to find out all detectable inconsistencies.
@@
 Because intermediate values are retained in the tree nodes after calculation they can be reused whenever the tree changes.
-More specifically, when a branch is added, only the values for the new branch itself and for the nodes from the branch top to the tree root need to be calculated.
+More specifically, when a branch is added, only the values of the new branch itself and of the nodes from the branch top to the tree root need to be calculated.
 When a branch is deleted, only the values for the nodes from the branch top to the tree root have to be recalculated.
 
-With their partial constraint checking algorithm Xu et \textit{al.} attained a time complexity between $O(n)$ for the worst case and $O(1)$ for the best case when a context was added to the set and $O(1)$ when a context was removed.
+With their partial constraint checking algorithm Xu et \textit{al.} attained a time complexity between $O(n)$ in the worst case and $O(1)$ in the best case when a context is added to the set and $O(1)$ when a context is removed.
 Compared to traditional constraint checking with an overall complexity of $O(n)$, this is a dramatical improvement.
-In their experiments Xu et \textit{al.} showed that their performance is 15 times better than the traditional approach and in a case study the inconsistency miss rate dropped from $52.2\%$ in traditional checking to $0.1\%$ with partial checking~\cite{xu:2010:PCC}.
+In their experiments Xu et \textit{al.} showed their performance is 15 times better than the traditional approach and in a case study the inconsistency miss rate dropped from $52.2\%$ in traditional checking to $0.1\%$ with partial checking~\cite{xu:2010:PCC}.
 
@@
 Now that we have an efficient method for detecting inconsistencies the task of resolving the conflicts remains.
-As discussed above the strategies for conflict resolution in literature are not very suited for pervasive computing because their assumptions do not apply or they require human participation~\cite{xu:2010:PCC}.
-What really is needed is an algorithm that in the case of a conflict between two or more contexts decides which context has the highest reliability and retains that context.
+As discussed above the strategies for conflict resolution in literature are not well suited for pervasive computing because their assumptions do not apply or they require human participation~\cite{xu:2010:PCC}.
+What is really needed is an algorithm that in the case of a conflict between two or more contexts decides which context has the highest reliability and retains that context.
 Bu et \textit{al.} show us that this is possible through extending the ontology based context model with additional information about the context's status and temporal properties~\cite{bu:2006:CCM}.
@@
 In pervasive computing traditionally first order logic is used to model the environment of an application.
-This results in a so called ontology based context model and every observation that does not exactly fit in this model results into a conflict that leads to misadjusted behavior in applications unless they are timely detected and resolved~\cite{xu:2010:PCC}.
+This results in a so called ontology based context model.
+Every observation that does not exactly fit in this model results into a conflict.
+This conflict can lead to misadjusted behavior in applications unless they are timely detected and resolved~\cite{xu:2010:PCC}.
 Because it is impossible to perfectly model the un-predictive environment in which context-aware applications run, it would be nice if the context model was more resilient to unexpected observations.
@@
 The probability of a higher-level context is calculated by simply multiplying the probabilities of the observed contexts.
-When a new context is added to the observation window, the intermediate calculation result stored at a node (the root in our case study) can simply be multiplied by de probability of the new observation in order to obtain the updated probability for a higher-level context.
+When a new context is added to the observation window, the intermediate calculation result stored at a node (the root in our case study) can simply be multiplied by the probability of the new observation in order to obtain the updated probability for a higher-level context.
 When a context disappears from the observation window, the intermediate result can simply be divided by the context's probability to obtain an updated probability for a higher-level context.
@@
 \section{Discussion}
-In this article we started with presenting partial constraint checking: an efficient algorithm for timely detecting inconsistencies in huge sets of contexts which change very frequently.
+In this article we started with presenting partial constraint checking: an efficient algorithm for timely detecting inconsistencies in huge sets of contexts which change frequently.
 Partial constraint checking was 15 times as efficient as the traditional greedy approach and reduced the conflict detection miss rate from 52.2\% to 0.1\%.
-This algorithm is clearly a dramatic improvement of the traditional approach and vital to any context aware application that has to handle high-frequently generated contexts.
+This algorithm is clearly a dramatic improvement of the traditional approach and vital to any context aware application that has to handle frequently generated contexts.
 

### 2011-04-07 paper/paper.tex
minor tweaks

@@
 
-Interestingly a fuzzy ontology has some tree-like structure that allows for very efficient incremental partial probability calculation (PPC).
+Interestingly a fuzzy ontology has some tree-like structure which allows for very efficient incremental partial probability calculation (PPC).
 The probability of a higher-level context is calculated by simply multiplying the probabilities of the observed contexts.
@@
 We have not shown an algorithm on how to do this efficiently as we don't know the formal definition of OWL at this point in time.
-However, with the definitions of OWL one can create a depth-first search algorithm that transforms an ontology in multiple CCTs (one for each leaf entity in the model).
+However, with the definitions of OWL one can create a depth-first search algorithm which transforms an ontology in multiple CCTs (one for each leaf entity in the model).
 
-After that we shed light on ways to resolve the detected conflicts and discussed a context inconsistency resolution algorithm that estimates the reliability of conflicting contexts and only retains the most reliable context from every conflict set.
+After that we shed light on ways to resolve the detected conflicts and discussed a context inconsistency resolution algorithm which estimates the reliability of conflicting contexts and only retains the most reliable context from every conflict set.
 Using this algorithm allows for timely conflict resolution at runtime without the need for human participation.

### 2011-04-12 paper/paper.tex
extend fuzzy section

@@
 
-\section{From Ontology to CCT}
-As stated above the Partial Constraint Checking (PCC) algorithm is much faster than Entire Constraint Checking due to the fact that a Consistency Computation Tree (CCT) is used to store the constraints belonging to a (set of) context(s).
-We also stated that the ontology based context model is the most promising type of model to capture context information.
-Although the context model appears as a tree (see Fig.
-\ref{fig:ont}), the PCC algorithm cannot be directly applied to it.
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=3.5in]{Ontology.eps}
-  \caption{An example of an ontology based context model Source:~\cite{bu:2006:CCM}}
-  \label{fig:ont}
-\end{figure}
-
-The model is actually a part of a larger ontology, but it is sufficient for this section.
-Now it needs to be transformed into a CCT for PCC.
-With a CCT the main focus should be on the context set of a single entity in the model.
-The transformation itself can be done automatically with a depth-first search algorithm, but there is no such algorithm available at this time.
-However, we can give a few examples of the CCT based on this ontology model.
-The context set of the entity \textit{Student} will be focused on.
-Lets say that the entity \textit{Student} is located in the \textit{Place} entity \textit{Road}, then the CCT will look as the upper tree in Fig.
-\ref{fig:cct1}.
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=3.5in]{smallCCT1.eps}
-  \caption{The CCTs of \textit{Student}}
-  \label{fig:cct1}
-\end{figure}
-
-If the system suddenly decides that \textit{Student} is located in a \textit{Lab}, then the tree will be updated to the lower tree.
-Note that the system can decide in a multitude of ways that \textit{Student} is located in the \textit{Lab} by for example invalidating the earlier constraint branch after a certain amount of time or by for example basing the new \textit{Place} on the information in a new context set.
-Also note that the leaf of a branch cannot contain an entity that is not available in the context model.
-So \textit{Student} cannot be located in, for example, \textit{Car}, because it is not part of the model.
-Even if the location in a context would be \textit{Car}, then the system would consider the location as an inconsistency in the context and detect it very quickly with PCC.
-
 \section{Context Inconsistency Resolution}
@@
 Every observation that does not exactly fit in this model results into a conflict.
-This conflict can lead to misadjusted behavior in applications unless they are timely detected and resolved~\cite{xu:2010:PCC}.
-Because it is impossible to perfectly model the un-predictive environment in which context-aware applications run, it would be nice if the context model was more resilient to unexpected observations.
-As we illustrate in the case study below, this can be obtained by using fuzzy ontologies.
+This conflict can lead to misadjusted behavior in applications unless it is timely detected and resolved~\cite{xu:2010:PCC}.
+Because it is impossible to perfectly model the unpredictable environment in which context-aware applications run, it would be nice if the context model was more resilient to unexpected observations.
+This resilience can be obtained by using a fuzzy ontology: a stochastic model representing lower level contexts (for instance sensory data) and their probabilities in the presence of higher level contexts (for instance user activities).
+The most simple approach to this would be using a hidden Markov Model\footnote{http://en.wikipedia.org/wikiHidden\_Markov\_model}: a statistical model of the environment with unobserved states (the higher level contexts) in which future states only depend on the present state.
+The use of such a model is illustrated in the case study below.
+
 \subsection{Case Study}
@@
 \end{figure}
+
+Observed Context Set 1: $[L_1, L_2, L_3, A_1, A_2]$
+\begin{align}
+                          Lecturing &= .8 * .8 * .8 * .15 * .15 * c_1\\
+                                    &= .01152 * c_1\\
+                                    &= 0.9998\\
+                            Working &= .05 * .05 * .05 * .15 * .15 * c_1\\
+                                    &= 0.000002813 * c_1\\
+                                    &= 0.0002
+\end{align}
+Observed Context Set 2: $[L_1, A_1, A_2, O_1, O_2]$
+\begin{align}
+                          Lecturing &= .8 * .15 * .15 * .05 * .05 * c_2\\
+                                    &= 0.000045 * c_2\\
+                                    &= 0.059\\
+                            Working &= .05 * .15 * .15 * .8 * .8 * c_2\\
+                                    &= 0.00072 * c_2\\
+                                    &= 0.941
+\end{align}
+
 Using this fuzzy ontology the relative probability of each specified higher-level context can be calculated from the contexts in the observation window.
@@
 
-Note that it is possible to extend the simple fuzzy ontology from the use case by specifying start and transition probabilities for the higher-level contexts, just as hidden Markov models\footnote{http://en.wikipedia.org/wikiHidden\_Markov\_model} do, and other information such as the expected lecture time window (fuzzified of course~\cite{Buckley1995245}).
+Note that it is possible to extend the simple fuzzy ontology from the use case by specifying start and transition probabilities for the higher-level contexts, just as hidden Markov models do, and other information such as the expected lecture time window (fuzzified of course~\cite{Buckley1995245}).
 
@@
 This algorithm is clearly a dramatic improvement of the traditional approach and vital to any context aware application that has to handle frequently generated contexts.
-
-Then we have shown examples of CCTs of entities in an ontology based context model.
-We have not shown an algorithm on how to do this efficiently as we don't know the formal definition of OWL at this point in time.
-However, with the definitions of OWL one can create a depth-first search algorithm which transforms an ontology in multiple CCTs (one for each leaf entity in the model).
 
@@
 \bibliography{paper}
-\newpage
-\appendix
-\section{Fuzzy Ontology Calculations}
-Observed Context Set 1: $[L_1, L_2, L_3, A_1, A_2]$
-\begin{align}
-                          Lecturing &= .8 * .8 * .8 * .15 * .15 * c_1\\
-                                    &= .01152 * c_1\\
-                                    &= 0.9998\\
-                            Working &= .05 * .05 * .05 * .15 * .15 * c_1\\
-                                    &= 0.000002813 * c_1\\
-                                    &= 0.0002
-\end{align}
-Observed Context Set 2: $[L_1, A_1, A_2, O_1, O_2]$
-\begin{align}
-                          Lecturing &= .8 * .15 * .15 * .05 * .05 * c_2\\
-                                    &= 0.000045 * c_2\\
-                                    &= 0.059\\
-                            Working &= .05 * .15 * .15 * .8 * .8 * c_2\\
-                                    &= 0.00072 * c_2\\
-                                    &= 0.941
-\end{align}
 \end{document}

### 2011-04-12 paper/paper.tex
extend case study

@@
 Every observation that does not exactly fit in this model results into a conflict.
-This conflict can lead to misadjusted behavior in applications unless it is timely detected and resolved~\cite{xu:2010:PCC}.
+This conflict can lead to misadjusted behavior in applications, unless it is timely detected and resolved~\cite{xu:2010:PCC}.
 Because it is impossible to perfectly model the unpredictable environment in which context-aware applications run, it would be nice if the context model was more resilient to unexpected observations.
@@
 \subsection{Case Study}
-Suppose we want to build a context-aware application that has certain notion of teacher's activities to assist them in the best possible way (for instance automatically opening slides when a lecture starts).
+Suppose we want to build a context-aware application that has a certain notion of teacher's activities to assist them in the best possible way (for instance automatically opening slides when a lecture starts).
 In the traditional approach we could build an ontology specifying where lectures take place and that a lecture starts when the teacher appears at the lectern.
-If now an unpredicted observation is made (sensor cross read or teacher momentarily leaves the room), an inconsistency occurs that has to be resolved for the application to proceed with normal operation.
-In the fuzzy ontology approach these unpredictable events can simply be modeled so that the ontology is more robust and always yields the most apt interpretation of the environment without conflict resolution.
-A simplified example of such an ontology is depicted in Fig.~\ref{fig:fuzzy}.
+If now an unpredicted observation is made (sensor cross read or teacher momentarily leaves the room), an inconsistency occurs that has to be resolved for the application to proceed with its normal operation.
+In the fuzzy ontology approach these unpredictable events can be modeled so that the ontology is more robust and always yields the most apt interpretation of the environment without the need for conflict resolution.
+A simplified hidden Markov model for this ontology is depicted in Fig.~\ref{fig:fuzzy}.
 \begin{figure}[htb]
@@
   \includegraphics[width=3.5in]{fuzzy}
-  \caption{Fuzzy ontology specifying teachers activities and their most probable location.}
+  \caption{Fuzzy ontology specifying teachers activities and the probabilities of different locations in the presence of this higher level context.}
   \label{fig:fuzzy}
 \end{figure}
+As the numbers in this model indicate, the most probable location of a teacher while lecturing is at the lectern (L).
+In the aisle (A) is less probable and at the office (O) is very unlikely.
+For the activity of performing other work (denoted as Working in the model), the probabilities are the other way around.
+This fuzzy ontology model can now be used to calculate the relative probability of each higher-level context (c.q.
+Lecturing and Working) based a set of low level contexts observed within a certain time window.
+A possible set of observations could be [$L_1$, $L_2$, $L_3$, $A_1$, $A_2$]: the teacher was observed three times at the lectern and twice in the aisle in this time window.
+The probability of the Lecturing activity can now be calculated by multiplying the probabilities of the observations in the presence of this higher level context\footnote{We multiply the results with a constant $c$ in order to obtain a valid probability value in the end}: $pLecturing = .80 * .80 * .80 * .15 * .15 * c_1 = .01152 * c_1 = 0.9998$.
+The probability for Working can be calculated in a similar way: $pWorking = .05 * .05 * .05 * .15 * .15 * c_1 = 0.000002813 * c_1 = 0.0002$.
+The probabilities indicate that the teacher is still lecturing, even though the teacher being observed in the aisle conflicts with being observed at the lectern.
+Another example of observations could be [$L_1$, $A_1$, $A_2$, $O_1$, $O_2$]: the teacher is observed at the lectern once, twice in the aisle and twice at the office.
+The probabilities for Lecturing and Working are calculated as follows: $pLecturing = .80 * .15 * .15 * .05 * .05 * c_2 = 0.000045 * c_2 = 0.059$ and $pWorking = .05 * .15 * .15 * .80 * .80 * c_2 = 0.00072 * c_2 = 0.941$.
+The probabilities now indicate that the teacher is doing work other than lecturing, even though the observation of the teacher at the lectern is definitely conflicting with the observations at the office.
+\subsection{Results}
+The case study shows that a fuzzy ontology allows us to always define the most probable higher-level context, regardless of any inconsistencies in the observed context set and without the need for conflict detection and resolution.
 
-Observed Context Set 1: $[L_1, L_2, L_3, A_1, A_2]$
-\begin{align}
-                          Lecturing &= .8 * .8 * .8 * .15 * .15 * c_1\\
-                                    &= .01152 * c_1\\
-                                    &= 0.9998\\
-                            Working &= .05 * .05 * .05 * .15 * .15 * c_1\\
-                                    &= 0.000002813 * c_1\\
-                                    &= 0.0002
-\end{align}
-Observed Context Set 2: $[L_1, A_1, A_2, O_1, O_2]$
-\begin{align}
-                          Lecturing &= .8 * .15 * .15 * .05 * .05 * c_2\\
-                                    &= 0.000045 * c_2\\
-                                    &= 0.059\\
-                            Working &= .05 * .15 * .15 * .8 * .8 * c_2\\
-                                    &= 0.00072 * c_2\\
-                                    &= 0.941
-\end{align}
+Another observation we can make is that the hidden Markov model for a fuzzy ontology has some tree-like structure.
+This structure allows for very efficient incremental partial probability calculation (PPC).
 
-Using this fuzzy ontology the relative probability of each specified higher-level context can be calculated from the contexts in the observation window.
-For instance the observation sequence [$L_1$, $L_2$, $L_3$, $A_1$, $A_2$] gives a relative probability of 0.9998 for `Lecturing' and 0.0002 for `Working', event though the observations are clearly conflicting, since the teacher clearly cannot be at the lectern and in the aisle at the same time.
-The sequence of [$L_1$, $A_1$, $A_2$, $O_1$, $O_2$] gives a 0.941 probability for `Working' and 0.059 for `Lecturing', even though the teacher strictly spoken cannot be at the lectern and in the office at the same time (see appendix for exact calculations).
-
-\subsection{Results}
-Regardless of any inconsistencies in the observed contexts a fuzzy ontology always yields the most probable higher-level context without the need for conflict detection and resolution.
-
-Interestingly a fuzzy ontology has some tree-like structure which allows for very efficient incremental partial probability calculation (PPC).
 The probability of a higher-level context is calculated by simply multiplying the probabilities of the observed contexts.

### 2011-04-12 paper/paper.tex
extend results section

@@
   \includegraphics[width=3.5in]{fuzzy}
-  \caption{Fuzzy ontology specifying teachers activities and the probabilities of different locations in the presence of this higher level context.}
+  \caption{Fuzzy ontology specifying a teacher's activities and the probabilities of different locations in the presence of these higher-level context.}
   \label{fig:fuzzy}
@@
 A possible set of observations could be [$L_1$, $L_2$, $L_3$, $A_1$, $A_2$]: the teacher was observed three times at the lectern and twice in the aisle in this time window.
-The probability of the Lecturing activity can now be calculated by multiplying the probabilities of the observations in the presence of this higher level context\footnote{We multiply the results with a constant $c$ in order to obtain a valid probability value in the end}: $pLecturing = .80 * .80 * .80 * .15 * .15 * c_1 = .01152 * c_1 = 0.9998$.
+The probability of the Lecturing activity can now be calculated by multiplying the probabilities of the observations in the presence of this higher level context\footnote{We multiply the results with a constant $c$ to obtain a valid probability value in the end}: $pLecturing = .80 * .80 * .80 * .15 * .15 * c_1 = .01152 * c_1 = 0.9998$.
 The probability for Working can be calculated in a similar way: $pWorking = .05 * .05 * .05 * .15 * .15 * c_1 = 0.000002813 * c_1 = 0.0002$.
@@
 \subsection{Results}
-The case study shows that a fuzzy ontology allows us to always define the most probable higher-level context, regardless of any inconsistencies in the observed context set and without the need for conflict detection and resolution.
+The case study shows that a fuzzy ontology allows us to always define the most probable higher-level context given the observations, regardless of any inconsistencies in the observed context set and without the need for conflict detection and resolution.
 
-Another observation we can make is that the hidden Markov model for a fuzzy ontology has some tree-like structure.
-This structure allows for very efficient incremental partial probability calculation (PPC).
+Another observation we can do is that the hidden Markov model for a fuzzy ontology has a tree-like structure.
+This structure allows for very efficient incremental Partial Probability Calculation (PPC).
+The PCC principle works as follows: the probability of a high-level context is calculated by multiplying the probabilities of its children contexts.
+When a new context is added to or removed from the observation set and thus from the tree, only the probabilities of the observation's ancestors in the tree up to the root have to be recalculated.
+In case of adding a context, the probability of an ancestor in the tree can be recalculated by simply multiplying its previous probability with the probability of the new or updated child.
+In case of removing a context, the probability is divided by the probability of the new or updated child.
+Because the recalculation only takes place in part of the tree and allows us to preserver previous calculations for later use, it is partial.
+And because this recalculation only happens in trees that contain the added or removed context as a leaf, the calculation is incremental.
+We illustrate the PPC process using an extension of the hidden Markov model from the case study (See Fig.~\ref{fig:fuzzy2}).
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=3.5in]{fuzzy2}
+  \caption{Fuzzy ontology specifying the Lecturing activity and the probabilities of different contexts in the presence of this higher-level context.}
+  \label{fig:fuzzy2}
+\end{figure}
+In this figure the usesSlides context is added to the observation set at some point.
+This change in the context set requires us to recalculate the probabilities of the higher-level contexts.
+For this we use PPC: we recalculate only the values of the ancestors if the usesSlides context (c.q.
+isPresenting and isLecturing).
+The probability of isPresenting is $.85 * .90$, because the usesSlides context is its only child.
+The probability of isLecturing has to be recalculated.
+This can be done by simply multiplying its previous probability with the probability of the new child isPresenting: $isLecturing = 0.0004104 * .90 * .85 = 0.000313956$\footnote{Note that this value has to be multiplied with a constant in order to get the real probability value}.
 
-The probability of a higher-level context is calculated by simply multiplying the probabilities of the observed contexts.
-When a new context is added to the observation window, the intermediate calculation result stored at a node (the root in our case study) can simply be multiplied by the probability of the new observation in order to obtain the updated probability for a higher-level context.
-When a context disappears from the observation window, the intermediate result can simply be divided by the context's probability to obtain an updated probability for a higher-level context.
+The time complexity of the PPC principle is related to the height of a hidden Markov tree, because recalculations only take place on the path from a leaf to the root.
+Since this height remains constant at runtime, the time complexity of adding or removing a context is $O(1)$.
 
-Note that it is possible to extend the simple fuzzy ontology from the use case by specifying start and transition probabilities for the higher-level contexts, just as hidden Markov models do, and other information such as the expected lecture time window (fuzzified of course~\cite{Buckley1995245}).
+It is possible to extend the hidden Markov model used in the case study by specifying start and transition probabilities for the higher-level contexts.
+With this extension the probability of a higher-level context does not solely depend on the contexts in the observation set, but also on the previous most probable higher-level context.
 
@@
 In this article we started with presenting partial constraint checking: an efficient algorithm for timely detecting inconsistencies in huge sets of contexts which change frequently.
-Partial constraint checking was 15 times as efficient as the traditional greedy approach and reduced the conflict detection miss rate from 52.2\% to 0.1\%.
+Partial constraint checking was 15 times more efficient than the traditional greedy approach and reduced the conflict detection miss rate from 52.2\% to 0.1\%.
 This algorithm is clearly a dramatic improvement of the traditional approach and vital to any context aware application that has to handle frequently generated contexts.
@@
 After that we shed light on ways to resolve the detected conflicts and discussed a context inconsistency resolution algorithm which estimates the reliability of conflicting contexts and only retains the most reliable context from every conflict set.
-Using this algorithm allows for timely conflict resolution at runtime without the need for human participation.
+This algorithm allows for timely conflict resolution at runtime without the need for human participation.
 The algorithm is a valuable addition to the research on conflict resolution in pervasive computing, but when applying it one has to verify the aptness of the heuristic used for context reliability estimations in the domain at hand.
@@
 Finally the use of fuzzy ontologies for modeling the environment of context-aware applications seems promising.
-By incorporating possible inconsistencies in the model the need for context inconsistency management vanishes, vastly reducing the complexity of the used middleware.
+By incorporating possible inconsistencies in the model, the need for context inconsistency management vanishes, vastly reducing the complexity of the used middleware.
 Fuzzy ontologies always yield the most probable higher-level contexts, regardless of the inconsistencies in the observed context set.
-In addition the calculation of the probabilities in a fuzzy ontology has great potential for optimization by using incremental partial probability calculation.
+In addition the calculation of the probabilities in a fuzzy ontology has great potential for optimization by using incremental Partial Probability Calculation.
 When using fuzzy ontologies one however has to take into account the required training of the system for obtaining well defined probabilities in the context model.

### 2011-04-12 paper/paper.tex
tweak

@@
 Apart from resolving context conflicts it is also possible to represent inconsistencies into the context model itself~\cite{ko:2009:IOFO}.
-In this paper we present a use case in which we explore the possibilities of incorporating inconsistencies into context models using fuzzy ontologies.
+In this paper we present a case study in which we explore the possibilities of incorporating inconsistencies into context models using fuzzy ontologies.
 } % end of abstract
@@
 %%%%%%%%%%%%%%%%%%%%%% START OF THE PAPER %%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2011-04-12 paper/paper.tex
rewrite introduction

@@
 \maketitle
+In pervasive computing applications use contexts to represent their changing environment and adapt their behavior to it.
+Due to environmental noises contexts can be imprecise or incorrect, resulting in context inconsistencies.
+These inconsistencies may set a pervasive application in a wrong state or misadjust its behavior.
+Therefore it is important to timely detect and resolve context inconsistencies.
 
-In pervasive computing, contexts are used to make applications perform a certain action.
-Contexts can be seen as pieces of environmental information, which the applications depend on.
-Sometimes contexts are not consistent due to cross reads and misreads.
-The correctness of the contexts can be checked by evaluating the consistency constraints associated to them.
-There are multiple ways to check for consistency constraints.
-Constraint checking techniques are split up in two classes: Non-incremental checking and incremental checking.
-Incremental checking also consists of two classes: Entire Constraint Checking and Partial Constraint Checking.
-Once inconsistent contexts have been detected, an algorithm can be used to select the correct contexts.
-The algorithms use specific data structures, like ontology models, in order to resolve the inconsistencies.
-However, certain conflict resolving algorithms are too slow for use in practice.
-This paper describes a way to use an ontology model in combination with the Partial Constraint Checking algorithm in order to detect context inconsistencies fast enough, such that it can be used in practice.
-Another approach to handling context inconsistencies is representing them into the context model, as opposed to resolving them.
-This can be done efficiently by using fuzzy ontologies in a tree like structure, as we show in a use case.
+In the next chapter we start with an overview of the existing solutions for handling context inconsistencies and argue why these solutions do not meet the requirements of pervasive applications.
+Next we present Partial Constraint Checking: an algorithm for constraint checking on huge sets of contexts that is far more efficient and effective than the existing approaches.
+In addition we discuss a Context Inconsistency Resolution algorithm that allows for resolving conflicting context sets without human intervention.
+Finally we propose a whole new approach to context inconsistencies: incorporating inconsistencies in to the context model by using fuzzy ontologies.
+We show that this approach makes conflict detection and resolution superfluous and has lots of potential for an efficient implementation using Partial Probability Calculation.
 

### 2011-04-17 paper/paper.tex
final review paper

@@
 %% please capitalize first letter and insert punctuation after last keyword
-\keywords{Pervasive Computing, Ontology Model, Context Lifecycle, Inconsistency Resolution.}
+\keywords{Pervasive Computing, Context Ontology Model, Partial Constraint Checking, Context Lifecycle, Context Inconsistency Resolution, Fuzzy OWL.}
 
@@
 Finally we propose a whole new approach to context inconsistencies: incorporating inconsistencies in to the context model by using fuzzy ontologies.
-We show that this approach makes conflict detection and resolution superfluous and has lots of potential for an efficient implementation using Partial Probability Calculation.
+We show that this approach makes conflict detection and resolution superfluous and has a lot of potential for an efficient implementation using Partial Probability Calculation.
 
@@
 None of the studies on context-awareness discusses a way for detecting context inconsistencies for reliable pervasive computing~\cite{xu:2010:PCC, bu:2006:CCM}.
-Even though other disciplines as artificial intelligence and software engineering conducted relate research, it does not provide adequate support for context inconsistency detection in ubiquitous computing.
+Even though other disciplines as artificial intelligence and software engineering conducted related research, it does not provide adequate support for context inconsistency detection in ubiquitous computing.
 In addition the strategies proposed in literature for resolving context conflicts are not suited for pervasive computing.
@@
 Other require human participation for conflict resolution, which is usually expensive and slow for pervasive computing~\cite{xu:2010:PCC}.
-Finally no research has been done on the potential of fuzzy ontologies to represent context inconsistencies in the environment instead of trying to resolve them~\cite{ko:2009:IOFO}.
+Finally no research has been done on the potential of fuzzy ontologies to represent inconsistencies in the environment or the perception of this environment instead of trying to resolve them~\cite{ko:2009:IOFO}.
 
@@
 An improvement to this would be incremental checking: only a subset of all constraints are checked, namely those that are affected by the specific change in the artifact set.
-But the real merit of Xu et \textit{al.} was replacing the traditional entire constraint checking approach by partial constraint checking based on a consistency computation tree~\cite{xu:2010:PCC}.
+But Xu et \textit{al.} made the most substantial progress by replacing the traditional entire constraint checking approach by partial constraint checking based on a consistency computation tree~\cite{xu:2010:PCC}.
 Their idea is that constraints can be represented as trees with nodes for logical operations and leaves for specific properties of contexts or context sets.
@@
 \end{figure}
-Because intermediate values are retained in the tree nodes after calculation they can be reused whenever the tree changes.
+Because intermediate values are retained in the tree nodes after calculation, they can be reused whenever the tree changes.
 More specifically, when a branch is added, only the values of the new branch itself and of the nodes from the branch top to the tree root need to be calculated.
@@
 \section{Context Inconsistency Resolution}
-Now that we have an efficient method for detecting inconsistencies the task of resolving the conflicts remains.
+Now that we have an efficient method for detecting inconsistencies, the task of resolving the conflicts remains.
 As discussed above the strategies for conflict resolution in literature are not well suited for pervasive computing because their assumptions do not apply or they require human participation~\cite{xu:2010:PCC}.
@@
 Bu et \textit{al.} show us that this is possible through extending the ontology based context model with additional information about the context's status and temporal properties~\cite{bu:2006:CCM}.
-More specifically they propose an algorithm that for every conflict set retains the context with the highest \textit{relative frequency}: frequency of context updates relative to update interval and context age (see Fig.~\ref{fig:cir}).
+More specifically they propose an algorithm that retains for every conflict set the context with the highest \textit{relative frequency}: frequency of context updates relative to update interval and context age (see Fig.~\ref{fig:cir}).
 \begin{figure}[htb]
@@
 This fuzzy ontology model can now be used to calculate the relative probability of each higher-level context (c.q.
-Lecturing and Working) based a set of low level contexts observed within a certain time window.
+Lecturing and Working) based on a set of low level contexts observed within a certain time window.
 A possible set of observations could be [$L_1$, $L_2$, $L_3$, $A_1$, $A_2$]: the teacher was observed three times at the lectern and twice in the aisle in this time window.
-The probability of the Lecturing activity can now be calculated by multiplying the probabilities of the observations in the presence of this higher level context\footnote{We multiply the results with a constant $c$ to obtain a valid probability value in the end}: $pLecturing = .80 * .80 * .80 * .15 * .15 * c_1 = .01152 * c_1 = 0.9998$.
+The probability of the Lecturing activity can now be calculated by multiplying the probabilities of the observations in the presence of this higher level context\footnote{We multiply the results with a constant $c$ to obtain a valid probability value in the end.}: $pLecturing = .80 * .80 * .80 * .15 * .15 * c_1 = .01152 * c_1 = 0.9998$.
 The probability for Working can be calculated in a similar way: $pWorking = .05 * .05 * .05 * .15 * .15 * c_1 = 0.000002813 * c_1 = 0.0002$.
@@
 In case of removing a context, the probability is divided by the probability of the new or updated child.
-Because the recalculation only takes place in part of the tree and allows us to preserver previous calculations for later use, it is partial.
+Because the recalculation only takes place in part of the tree and allows us to preserve previous calculations for later use, it is partial.
 And because this recalculation only happens in trees that contain the added or removed context as a leaf, the calculation is incremental.
@@
 Partial constraint checking was 15 times more efficient than the traditional greedy approach and reduced the conflict detection miss rate from 52.2\% to 0.1\%.
-This algorithm is clearly a dramatic improvement of the traditional approach and vital to any context aware application that has to handle frequently generated contexts.
+This algorithm is clearly a dramatic improvement of the traditional approach and vital to any context-aware application that has to handle frequently generated contexts.
 

### 2011-04-23 paper/paper.tex
tweak

@@
 An improvement to this would be incremental checking: only a subset of all constraints are checked, namely those that are affected by the specific change in the artifact set.
-But Xu et \textit{al.} made the most substantial progress by replacing the traditional entire constraint checking approach by partial constraint checking based on a consistency computation tree~\cite{xu:2010:PCC}.
+But Xu \textit{et al.} made the most substantial progress by replacing the traditional entire constraint checking approach by partial constraint checking based on a consistency computation tree~\cite{xu:2010:PCC}.
 Their idea is that constraints can be represented as trees with nodes for logical operations and leaves for specific properties of contexts or context sets.
@@
 
-With their partial constraint checking algorithm Xu et \textit{al.} attained a time complexity between $O(n)$ in the worst case and $O(1)$ in the best case when a context is added to the set and $O(1)$ when a context is removed.
+With their partial constraint checking algorithm Xu \textit{et al.} attained a time complexity between $O(n)$ in the worst case and $O(1)$ in the best case when a context is added to the set and $O(1)$ when a context is removed.
 Compared to traditional constraint checking with an overall complexity of $O(n)$, this is a dramatical improvement.
-In their experiments Xu et \textit{al.} showed their performance is 15 times better than the traditional approach and in a case study the inconsistency miss rate dropped from $52.2\%$ in traditional checking to $0.1\%$ with partial checking~\cite{xu:2010:PCC}.
+In their experiments Xu \textit{et al.} showed their performance is 15 times better than the traditional approach and in a case study the inconsistency miss rate dropped from $52.2\%$ in traditional checking to $0.1\%$ with partial checking~\cite{xu:2010:PCC}.
 
@@
 What is really needed is an algorithm that in the case of a conflict between two or more contexts decides which context has the highest reliability and retains that context.
-Bu et \textit{al.} show us that this is possible through extending the ontology based context model with additional information about the context's status and temporal properties~\cite{bu:2006:CCM}.
+Bu \textit{et al.} show us that this is possible through extending the ontology based context model with additional information about the context's status and temporal properties~\cite{bu:2006:CCM}.
 More specifically they propose an algorithm that retains for every conflict set the context with the highest \textit{relative frequency}: frequency of context updates relative to update interval and context age (see Fig.~\ref{fig:cir}).

### 2011-05-12 paper/paper.tex
miinor tweaks

@@
 In conclusion we can say that the partial constraint checking algorithm can dramatically improve the performance of context-aware applications where context consistency management is needed.
-With this performance improvement we get an impressive reduction of missed context inconsistencies for free.
+And with this performance improvement we get an impressive reduction of missed context inconsistencies for free.
 The context inconsistency resolution algorithm is a good solution in most domains for timely resolving context conflicts without human intervention.
-The fuzzy ontology approach seems a promising alternative to traditional context modeling but needs extensive further research in order to determine its real value in context-aware applications.
+The fuzzy ontology approach seems a promising alternative to traditional context modeling, but needs extensive further research in order to determine its real value for context-aware applications.
 
